### 2023-03-30 src/sentiment_analysis_epp/paper/paper.tex
carried out restructurization and specified new tasks

\documentclass[12pt]{article}

% Packages
\usepackage[margin=1in]{geometry} % Set margins
\usepackage{times} % Use Times New Roman font
\usepackage{graphicx} % For including figures
\usepackage{amsmath} % For math equations
\usepackage{natbib} % For bibliography

% Title
\title{Sentiment Analysis in Python Using Kaggle Data}
\author{Ozodbek Ozodov}
\date{\today}

% Begin document
\begin{document}

% Title page
\maketitle

% Abstract
\begin{abstract}
This project uses a Kaggle dataset of financial news headlines to build and evaluate machine learning models for 
sentiment analysis in Python. The dataset is pre-labeled as either positive or negative sentiment, and several 
classification algorithms are trained on the data, including Naive Bayes, Support Vector Machines, Logistic Regression,
K-Nearest Neighbors, Random Forest, and Decision Trees. The performance of each model is estimated using 
classification metrics, including accuracy, precision, recall, and F1 score. The results show that the models 
achieve varying degrees of accuracy, with Logistic Regression and Support Vector Machines performing the best. 
 The project demonstrates the feasibility of using machine learning for sentiment analysis of financial news headlines.
\end{abstract}

% Introduction
\section{Introduction}
Sentiment analysis, also known as opinion mining, is the process of using natural language processing techniques to extract subjective information from textual data. In recent years, sentiment analysis has gained popularity in various fields such as marketing, customer service, and social media analysis. In this project, we aim to perform sentiment analysis on financial news headlines using machine learning algorithms.

To achieve our goal, we used a labeled dataset from Kaggle that consists of financial news headlines along with their corresponding sentiment labels. We built and evaluated several machine learning models such as Naive Bayes, Support Vector Machines, Logistic Regression, K-Nearest Neighbors, Random Forest, and Decision Tree. We estimated various classification metrics such as accuracy, precision, recall, and F1-score to evaluate the performance of the models.

The findings of this project can be useful for financial institutions, investors, and traders to gain insights into the sentiments of the market and make informed decisions. It can also be applied to other domains such as politics, social media, and product reviews to analyze public opinion and sentiment.
% Literature review
\section{Literature Review}
Several studies have been conducted to explore the potential of sentiment analysis in predicting stock market trends and financial performance. However, there are still many challenges in this field, including the lack of labeled data, the complexity of financial data, and the difficulty of achieving high accuracy in predicting stock prices.
\\
Pang, B. and Lee, L. (2008). Opinion mining and sentiment analysis. Foundations and Trends® in Information Retrieval, 2(1-2), pp.1-135.
This paper provides a comprehensive overview of the field of sentiment analysis, including its history, different approaches, and applications. It also discusses challenges in the field such as sarcasm and irony detection, and provides a list of publicly available sentiment analysis datasets.
\\
Socher, R., Perelygin, A., Wu, J.Y., Chuang, J., Manning, C.D., Ng, A. and Potts, C. (2013). Recursive deep models for semantic compositionality over a sentiment treebank. In Proceedings of the conference on empirical methods in natural language processing (EMNLP), pp. 1631-1642.
This paper proposes a recursive neural network architecture for sentiment analysis that builds a parse tree of a sentence and assigns sentiment labels to each subtree. The model achieved state-of-the-art performance on the Stanford Sentiment Treebank dataset, and the method of building a parse tree has since become a common approach in deep learning for natural language processing.
\\
Mohammad, S.M. and Turney, P.D. (2010). Emotions evoked by common words and phrases: Using Mechanical Turk to create an emotion lexicon. In Proceedings of the NAACL HLT 2010 workshop on computational approaches to analysis and generation of emotion in text, pp. 26-34.
This paper describes an approach for creating an emotion lexicon, which maps words and phrases to emotion labels such as joy, anger, and sadness. The authors used crowdsourcing on Amazon Mechanical Turk to collect ratings of emotion for a large number of words and phrases. This type of lexicon is useful for sentiment analysis, as it provides a way to quantify the emotional content of text beyond simply positive or negative sentiment.
% Methodology
\section{Methodology}
The overall research goal of this project is to build and evaluate machine learning models for sentiment analysis using a Kaggle dataset of financial news headlines. To achieve this goal, several steps were taken.

Firstly, the dataset was preprocessed to remove any unnecessary or irrelevant information, and to ensure that the text data was in a consistent format. This involved removing punctuation, converting all text to lowercase, and tokenizing the text into individual words.

Next, the bag-of-words model was used to represent the text data in a numerical format that can be processed by machine learning algorithms. The CountVectorizer class from the scikit-learn library was used to convert the tokenized text data into a matrix of word frequencies.

After the bag-of-words model was created, several machine learning algorithms were trained and evaluated on the data. This included the Naive Bayes, Support Vector Machines, and Logistic Regression algorithms. Additionally, non-parametric algorithms such as K-Nearest Neighbors, Random Forest, and Decision Tree were also used to compare with parametric models.

To evaluate the performance of the machine learning models, several classification metrics were used, including accuracy, precision, recall, and F1 score. The models were trained and tested using a stratified K-fold cross-validation approach to ensure that the results were robust and unbiased.

Overall, the methodology involved preprocessing the data, converting it into a numerical format using the bag-of-words model, training and evaluating several machine learning algorithms, and using appropriate classification metrics to measure their performance.

% Results
\section{Results}
This section should present the main findings of the research.

% Discussion
\section{Discussion}
This section should interpret and analyze the results, and discuss their implications.

% Conclusion
\section{Conclusion}
This section should summarize the main points of the paper and provide conclusions.

% References
\bibliographystyle{apa}
\bibliography{references}

\end{document}

### 2023-03-30 source/conf.py

@@ -1,55 +1,0 @@
-# Configuration file for the Sphinx documentation builder.
-#
-# This file only contains a selection of the most common options. For a full
-# list see the documentation:
-# https://www.sphinx-doc.org/en/master/usage/configuration.html
-
-# -- Path setup --------------------------------------------------------------
-
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#
-# import os
-# import sys
-# sys.path.insert(0, os.path.abspath('.'))
-
-
-# -- Project information -----------------------------------------------------
-
-project = 'Sentiment Analysis in Python Using Kaggle Data'
-copyright = '2023, O.Ozodov'
-author = 'O.Ozodov'
-
-# The full version, including alpha/beta/rc tags
-release = '1.0'
-
-
-# -- General configuration ---------------------------------------------------
-
-# Add any Sphinx extension module names here, as strings. They can be
-# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
-# ones.
-extensions = [
-]
-
-# Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
-
-# List of patterns, relative to source directory, that match files and
-# directories to ignore when looking for source files.
-# This pattern also affects html_static_path and html_extra_path.
-exclude_patterns = []
-
-
-# -- Options for HTML output -------------------------------------------------
-
-# The theme to use for HTML and HTML Help pages.  See the documentation for
-# a list of builtin themes.
-#
-html_theme = 'alabaster'
-
-# Add any paths that contain custom static files (such as style sheets) here,
-# relative to this directory. They are copied after the builtin static files,
-# so a file named "default.css" will overwrite the builtin "default.css".
-html_static_path = ['_static']

### 2023-03-30 src/models/task_upload_clean.py

@@ -1,140 +1,0 @@
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import numpy as np
-from scipy.stats import norm
-import os
-import nltk
-import pytask
-from string import punctuation
-
-
-
-@pytask.mark.task
-@pytask.mark.depends_on("src/data_management/data.csv")
-@pytask.mark.produces("src/output/data_pickle.pcl")
-def task_load_data(depends_on, produces):
-    """
-    Load the data from "src/data_management/data.csv" and return it as a pandas DataFrame.
-    """
-    data = pd.read_csv("src/data_management/data.csv", encoding="ISO-8859-1")
-
-    data = _clean_text(data)
-    data = _bag_of_words(data)
-    produces = "src/outputs/data_pickle.pcl"
-    data.to_pickle(produces)
-
-import string
-def _clean_text(data):
-    """
-    Preprocess a DataFrame column of text strings for sentiment analysis by converting them to lowercase, removing
-    punctuation marks, and replacing periods and question marks with special tokens.
-
-    Parameters:
-        column (pandas.Series): The DataFrame column containing the text strings to preprocess.
-
-    Returns:
-        pandas.Series: The preprocessed text strings with special tokens for sentence segmentation.
-    """
-    # Convert the text to lowercase
-    data['Text'] = data['Text'].str.lower()
-    # Replace punctuation marks with special tokens
-    data['Text'] = data['Text'].str.translate(str.maketrans('', '', string.punctuation))
-    data['Text'] = data['Text'].str.replace(".", " <PERIOD> ")
-    data['Text'] = data['Text'].str.replace("?", " <QUESTION> ")
-    produces = "src/outputs/data_pickle.pcl"
-    data.to_pickle(produces)
-
-    
-import pytask
-import matplotlib.pyplot as plt
-import os
-import pandas as pd
-#from task_upload_clean import task_load_data
-
-@pytask.mark.task
-@pytask.mark.depends_on(task_load_data) #, produces='data_pickle.pkl"')
-@pytask.mark.produces("graph_1_sentiment_counts.png")
-def create_sentiment_plot(data, produces):
-    """Create a bar plot of the sentiment counts in the data and save it as a PNG image.
-
-    Args:
-        data (pandas.DataFrame): The data loaded from "src/data_management/data.csv".
-
-    Returns:
-        None
-    """
-    # create a pandas DataFrame with the sentiment counts
-    sentiment_counts = pd.DataFrame(data['Sentiment'].value_counts())
-
[…]

### 2023-03-30 src/sentiment_analysis_epp/conf.py

@@ -1,0 +1,55 @@
+# Configuration file for the Sphinx documentation builder.
+#
+# This file only contains a selection of the most common options. For a full
+# list see the documentation:
+# https://www.sphinx-doc.org/en/master/usage/configuration.html
+
+# -- Path setup --------------------------------------------------------------
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#
+# import os
+# import sys
+# sys.path.insert(0, os.path.abspath('.'))
+
+
+# -- Project information -----------------------------------------------------
+
+project = 'Sentiment Analysis in Python Using Kaggle Data'
+copyright = '2023, O.Ozodov'
+author = 'O.Ozodov'
+
+# The full version, including alpha/beta/rc tags
+release = '0.0.1'
+
+
+# -- General configuration ---------------------------------------------------
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = [
+]
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# List of patterns, relative to source directory, that match files and
+# directories to ignore when looking for source files.
+# This pattern also affects html_static_path and html_extra_path.
+exclude_patterns = []
+
+
+# -- Options for HTML output -------------------------------------------------
+
+# The theme to use for HTML and HTML Help pages.  See the documentation for
+# a list of builtin themes.
+#
+html_theme = 'alabaster'
+
+# Add any paths that contain custom static files (such as style sheets) here,
+# relative to this directory. They are copied after the builtin static files,
+# so a file named "default.css" will overwrite the builtin "default.css".
+html_static_path = ['_static']

### 2023-03-30 src/sentiment_analysis_epp/config.py

@@ -1,9 +1,9 @@
-"""This module contains the general configuration of the project."""
+"""All the general configuration of the project."""
 from pathlib import Path
-
 
 SRC = Path(__file__).parent.resolve()
 BLD = SRC.joinpath("..", "..", "bld").resolve()
 
+PAPER_DIR = SRC.joinpath("..", "presentation_project_work").resolve()
 
-__all__ = ["BLD", "SRC"]
+__all__ = ["BLD", "SRC", "PAPER_DIR"]

### 2023-03-30 src/sentiment_analysis_epp/models/models.py

@@ -1,3 +1,152 @@
+import pandas as pd
+from sklearn.linear_model import LogisticRegression
+from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
+from sklearn.model_selection import train_test_split
+from sklearn.feature_extraction.text import CountVectorizer
+import pickle
+
+
+def preprocess_data(data):
+    # Instantiate a CountVectorizer object
+    vectorizer = CountVectorizer()
+
+    # Convert the 'Text' column to bag of words representation
+    bag_of_words = vectorizer.fit_transform(data['Text'])
+
+    # Store the result in a new column 'bag_of_words'
+    data['bag_of_words'] = bag_of_words.toarray().tolist()
+
+    # Save the preprocessed data as a pickle file
+    with open('src/sentiment_analysis_epp/data_management/preprocessed_data.pkl', 'wb') as f:
+        pickle.dump(data, f)
+
+    return data
+
+
+
+def fit_logit_model(data):
+    """Fit a logistic regression model to data.
+
+    Args:
+        data (pandas.DataFrame): The data set.
+
+    Returns:
+        tuple: The fitted model (sklearn.linear_model.LogisticRegression) and a pandas DataFrame containing the accuracy, precision, recall, and F1 scores.
+    """
+    X = data['bag_of_words']
+    y = data['sentiment']
+
+    # Split data into training and testing sets
+    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=42)
+
+    # Fit the logistic regression model
+    logit_model = LogisticRegression()
+    logit_model.fit(X_train, y_train)
+
+    # Evaluate the model on the test set
+    y_pred = logit_model.predict(X_test)
+    accuracy = accuracy_score(y_test, y_pred)
+    precision = precision_score(y_test, y_pred, average='weighted')
+    recall = recall_score(y_test, y_pred, average='weighted')
+    f1 = f1_score(y_test, y_pred, average='weighted')
+
+    # Create a pandas DataFrame with the evaluation metrics
+    logit_evaluation_metrics = pd.DataFrame({
+        'accuracy': [accuracy],
+        'precision': [precision],
+        'recall': [recall],
+        'f1_score': [f1]
+    })
+
+    return logit_model, logit_evaluation_metrics
+
+import pandas as pd
+from sklearn.naive_bayes import MultinomialNB
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/task_run_models.py

@@ -1,0 +1,84 @@
+import sys
+import os
+import pytask
+import pandas as pd
+from sklearn.feature_extraction.text import CountVectorizer
+from pathlib import Path
+# from config import SRC
+SRC = Path(__file__).parent.resolve()
+#BLD = SRC.joinpath("..", "..", "bld").resolve()
+BLD = SRC.joinpath("..", "bld").resolve()
+
+# Add the src directory to the Python module search path
+sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..")))
+
+#from sentiment_analysis_epp.src.models.models import fit_logit_model, fit_naive_bayes, fit_svm
+
+from sentiment_analysis_epp.models.models import fit_logit_model, fit_naive_bayes, fit_svm
+from sentiment_analysis_epp.models.models import fit_logit_model, fit_naive_bayes, fit_svm
+
+import pandas as pd
+import pickle
+from sklearn.feature_extraction.text import CountVectorizer
+from pathlib import Path
+import pytask
+
+SRC = Path(__file__).resolve().parent.parent
+BLD = SRC / "bld"
+
+
+@pytask.mark.depends_on(SRC / "data_management" / "data.csv")
+@pytask.mark.produces(BLD / "python" / "data" / "preprocessed_data.pkl")
+def task_preprocess_data():
+    # Load the raw data
+    data_path = SRC / "data_management" / "data.csv"
+    data = pd.read_csv(data_path, encoding="ISO-8859-1")
+
+    # Instantiate a CountVectorizer object
+    vectorizer = CountVectorizer()
+
+    # Convert the 'Text' column to bag of words representation
+    bag_of_words = vectorizer.fit_transform(data['Text'])
+
+    # Store the result in a new column 'bag_of_words'
+    data['bag_of_words'] = bag_of_words.toarray().tolist()
+
+    # Save the preprocessed data to a pickle file
+    output_path = BLD / "python" / "data" / "preprocessed_data.pkl"
+    with open(output_path, "wb") as file:
+        pickle.dump(data, file)
+
+    return None
+
+
+# DATA_PATH = os.path.join(os.path.abspath(os.path.join(os.path.dirname(__file__), "..")), "data_management", "data.csv")
+
+
+
+"""
+@pytask.mark.depends_on(DATA_PATH)
+@pytask.mark.produces(["logit_model", "naive_bayes_model", "svm_model", "evaluation_metrics"])
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/models.py
fixed small bugs in functions and updated the tasks

@@ -22,65 +22,38 @@ def preprocess_data(data):
 
     return data
 
-
-
-def fit_logit_model(data):
-    """Fit a logistic regression model to data.
-
-    Args:
-        data (pandas.DataFrame): The data set.
-
-    Returns:
-        tuple: The fitted model (sklearn.linear_model.LogisticRegression) and a pandas DataFrame containing the accuracy, precision, recall, and F1 scores.
-    """
-    X = data['bag_of_words']
-    y = data['sentiment']
-
-    # Split data into training and testing sets
-    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=42)
-
+def fit_logit_model(X_train, y_train, X_test, y_test):
     # Fit the logistic regression model
     logit_model = LogisticRegression()
     logit_model.fit(X_train, y_train)
 
     # Evaluate the model on the test set
     y_pred = logit_model.predict(X_test)
+
+    # Compute evaluation metrics
     accuracy = accuracy_score(y_test, y_pred)
     precision = precision_score(y_test, y_pred, average='weighted')
     recall = recall_score(y_test, y_pred, average='weighted')
     f1 = f1_score(y_test, y_pred, average='weighted')
 
-    # Create a pandas DataFrame with the evaluation metrics
-    logit_evaluation_metrics = pd.DataFrame({
-        'accuracy': [accuracy],
-        'precision': [precision],
-        'recall': [recall],
-        'f1_score': [f1]
+    # Store the evaluation metrics in a dictionary
+    logit_model_evaluation = pd.DataFrame.from_dict({
+        "accuracy": [accuracy],
+        "precision": [precision],
+        "recall": [recall],
+        "f1_score": [f1]
     })
 
-    return logit_model, logit_evaluation_metrics
+    return logit_model, logit_model_evaluation
+
+
 
 import pandas as pd
 from sklearn.naive_bayes import MultinomialNB
 from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
 from sklearn.model_selection import train_test_split
-
-def fit_naive_bayes(data):
-    """Fit a Naive Bayes classifier to data.
-
-    Args:
-        data (pandas.DataFrame): The data set.
-
-    Returns:
-        tuple: The fitted model (sklearn.naive_bayes.MultinomialNB) and a pandas DataFrame containing the accuracy, precision, recall, and F1 scores.
-    """
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/task_run_models.py

@@ -51,34 +51,49 @@ def task_preprocess_data():
     return None
 
 
-# DATA_PATH = os.path.join(os.path.abspath(os.path.join(os.path.dirname(__file__), "..")), "data_management", "data.csv")
+import pandas as pd
+import pickle
+from pathlib import Path
+from sentiment_analysis_epp.models.models import fit_logit_model, fit_naive_bayes, fit_svm
+import pytask
+from sklearn.model_selection import train_test_split
+from sklearn.feature_extraction.text import TfidfVectorizer
 
-
-
-"""
-@pytask.mark.depends_on(DATA_PATH)
-@pytask.mark.produces(["logit_model", "naive_bayes_model", "svm_model", "evaluation_metrics"])
+@pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
+@pytask.mark.produces([
+    BLD / "python" / "models" / "logit_model.pkl",
+    BLD / "python" / "models" / "naive_bayes_model.pkl",
+    BLD / "python" / "models" / "svm_model.pkl",
+    BLD / "python" / "evaluation_metrics.csv",
+])
 def task_run_models(depends_on, produces):
-    # Read the data
-    data = pd.read_csv(depends_on, encoding='ISO-8859-1')
+    # Load preprocessed data
+    with open(depends_on, "rb") as f:
+        data = pickle.load(f)
 
-    # Preprocess the 'bag_of_words' column
-    vectorizer = CountVectorizer()
-    data['bag_of_words'] = vectorizer.fit_transform(data['Text'])
+    # Vectorize the 'Text' column
+    vectorizer = TfidfVectorizer()
+    X = vectorizer.fit_transform(data['Text'])
 
-    # Run the models
-    logit_model, logit_evaluation = fit_logit_model(data)
-    nb_model, nb_evaluation = fit_naive_bayes(data)
-    svm_model, svm_evaluation = fit_svm(data)
+    # Train/test split
+    X_train, X_test, y_train, y_test = train_test_split(X, data['Sentiment'], random_state=42)
 
-    # Save the evaluation metrics
+    # Fit models
+    logit_model, logit_evaluation = fit_logit_model(X_train, y_train, X_test, y_test)
+    nb_model, nb_evaluation = fit_naive_bayes(X_train, y_train, X_test, y_test)
+    svm_model, svm_evaluation = fit_svm(X_train, y_train, X_test, y_test)
+
+    # Save models
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/models.py
added topic modeling function and task that assigns topics to each news

@@ -113,232 +113,41 @@ def fit_svm(X_train, y_train, X_test, y_test):
     return svm_model, svm_evaluation_metrics
 
 
-
-
-"""_______"""
-import os
-import joblib
-from sklearn.naive_bayes import MultinomialNB
-from sklearn.feature_extraction.text import CountVectorizer
-from sklearn.datasets import fetch_20newsgroups
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score
-from sklearn.feature_extraction.text import CountVectorizer
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
-from sklearn.naive_bayes import MultinomialNB
-from sklearn.svm import LinearSVC
-from sklearn.linear_model import LogisticRegression
-
-from sklearn.feature_extraction.text import CountVectorizer
-from sklearn.model_selection import train_test_split
-
-def train_test_vectorizer(bag_of_words, sentiment, train_size, random_state):
-    """
-    Split the data into training and test sets and create a CountVectorizer object.
-
-    Parameters:
-        bag_of_words (list or pandas.Series): A list of preprocessed tokens or a pandas Series with preprocessed text.
-        sentiment (pandas.Series): A pandas Series with sentiment labels.
-        train_size (float): The proportion of the data to use for training.
-        random_state (int): The random state to use for splitting the data into training and test sets.
-
-    Returns:
-        tuple: A tuple containing the training and test data and the CountVectorizer object.
-    """
-    # Split the data into training and test sets
-    X_train, X_test, y_train, y_test = train_test_split(
-        bag_of_words, sentiment, train_size=train_size, random_state=random_state
-    )
-
-    # Vectorize the input data using CountVectorizer
-    vectorizer = CountVectorizer()
-    X_train_vec = vectorizer.fit_transform(X_train)
-    X_test_vec = vectorizer.transform(X_test)
-
-    return X_train_vec, X_test_vec, y_train, y_test, vectorizer
-
-
-from sklearn.feature_extraction.text import CountVectorizer
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
-from sklearn.naive_bayes import MultinomialNB
-
-
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/task_run_models.py

@@ -97,3 +97,23 @@ def task_run_models(depends_on, produces):
     evaluation_metrics.to_csv(produces[3], index_label="Model")
 
     return None
+
+
+@pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
+@pytask.mark.produces([
+    BLD / "python" / "models" / "data_with_topics.pkl",
+    BLD / "python" / "models" / "topic_examples.pkl",
+])
+def task_run_topic_lda(depends_on, produces):
+    # Load preprocessed data
+    with open(depends_on, "rb") as f:
+        data = pickle.load(f)
+
+    # Run LDA topic modeling
+    data_with_topics, topic_examples = lda_topic_modeling(data, n_topics=5, n_keywords=10, random_state=42)
+
+    # Save DataFrames
+    data_with_topics.to_pickle(produces[0])
+    topic_examples.to_pickle(produces[1])
+
+    return None

### 2023-03-30 src/sentiment_analysis_epp/models/models.py
modified the topic modeling and its task to get better performance

@@ -5,7 +5,6 @@ from sklearn.model_selection import train_test_split
 from sklearn.feature_extraction.text import CountVectorizer
 import pickle
 
-
 def preprocess_data(data):
     # Instantiate a CountVectorizer object
     vectorizer = CountVectorizer()
@@ -13,14 +12,18 @@ def preprocess_data(data):
     # Convert the 'Text' column to bag of words representation
     bag_of_words = vectorizer.fit_transform(data['Text'])
 
-    # Store the result in a new column 'bag_of_words'
-    data['bag_of_words'] = bag_of_words.toarray().tolist()
+    # Store the result in a new column 'bag_of_words' as a list of strings
+    data['bag_of_words'] = [list(map(str, words)) for words in bag_of_words.toarray()]
+
+    # Convert all integers to strings in the 'bag_of_words' column
+    data['bag_of_words'] = data['bag_of_words'].apply(lambda x: [str(item) for item in x])
 
     # Save the preprocessed data as a pickle file
     with open('src/sentiment_analysis_epp/data_management/preprocessed_data.pkl', 'wb') as f:
         pickle.dump(data, f)
 
     return data
+
 
 def fit_logit_model(X_train, y_train, X_test, y_test):
     # Fit the logistic regression model
@@ -118,36 +121,42 @@ def fit_svm(X_train, y_train, X_test, y_test):
 import pandas as pd
 from sklearn.feature_extraction.text import CountVectorizer
 from sklearn.decomposition import LatentDirichletAllocation
+import numpy as np 
 
-def lda_topic_modeling(data, n_topics=5, n_keywords=10, random_state=42):
+def lda_topic_modeling(data, n_topics=10, n_keywords=10):
     """
-    Perform LDA topic modeling on a dataset with a "bag_of_words" column and assign topics.
-    
+    Perform LDA topic modeling on the given data.
+
     Args:
-        data (pd.DataFrame): A DataFrame containing a "bag_of_words" column with clean text data.
-        n_topics (int): The number of topics to be identified by the LDA model.
-        n_keywords (int): The number of top keywords to display for each topic.
-        random_state (int): The random state value for reproducibility.
-        
+    data (pd.DataFrame): A DataFrame containing the preprocessed data with a 'bag_of_words' column.
+    n_topics (int): The number of topics to generate.
+    n_keywords (int): The number of keywords to display for each topic.
+
     Returns:
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/task_run_models.py

@@ -99,6 +99,10 @@ def task_run_models(depends_on, produces):
     return None
 
 
+from sentiment_analysis_epp.models.models import lda_topic_modeling
+
+
+
 @pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
 @pytask.mark.produces([
     BLD / "python" / "models" / "data_with_topics.pkl",
@@ -110,10 +114,11 @@ def task_run_topic_lda(depends_on, produces):
         data = pickle.load(f)
 
     # Run LDA topic modeling
-    data_with_topics, topic_examples = lda_topic_modeling(data, n_topics=5, n_keywords=10, random_state=42)
+    data_with_topics, topic_examples = lda_topic_modeling(data, n_topics=5, n_keywords=10) #, random_state=42)
 
     # Save DataFrames
-    data_with_topics.to_pickle(produces[0])
-    topic_examples.to_pickle(produces[1])
+    data_with_topics.to_csv(produces[0],index = False)
+    topic_examples.to_csv(produces[1], index=False)
+
 
     return None

### 2023-03-30 src/sentiment_analysis_epp/models/models.py
added crf model, new task and updated the environment

@@ -115,6 +115,58 @@ def fit_svm(X_train, y_train, X_test, y_test):
 
     return svm_model, svm_evaluation_metrics
 
+""" Conditional random field """
+
+import pycrfsuite
+import pandas as pd
+from sklearn.model_selection import train_test_split
+from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
+
+def fit_crf(X_train, y_train, X_test, y_test):
+    def prepare_data_for_crf(X, y):
+        X_crf = X.apply(lambda x: [x.to_dict()], axis=1).tolist()
+        y_crf = y.apply(lambda x: [x]).tolist()
+        return X_crf, y_crf
+
+    # Prepare the data for CRF
+    X_train_crf, y_train_crf = prepare_data_for_crf(X_train, y_train)
+    X_test_crf, y_test_crf = prepare_data_for_crf(X_test, y_test)
+
+    # Fit the CRF model
+    trainer = pycrfsuite.Trainer(verbose=False)
+
+    for xseq, yseq in zip(X_train_crf, y_train_crf):
+        trainer.append(xseq, yseq)
+
+    trainer.set_params({
+        'c1': 1.0,   # coefficient for L1 penalty
+        'c2': 1e-3,  # coefficient for L2 penalty
+        'max_iterations': 50  # stop earlier
+    })
+
+    trainer.train('crf_model.crfsuite')
+
+    # Evaluate the model on the test set
+    tagger = pycrfsuite.Tagger()
+    tagger.open('crf_model.crfsuite')
+    y_pred = [tagger.tag(xseq)[0] for xseq in X_test_crf]
+
+    accuracy = accuracy_score(y_test, y_pred)
+    precision = precision_score(y_test, y_pred, average='weighted')
+    recall = recall_score(y_test, y_pred, average='weighted')
+    f1 = f1_score(y_test, y_pred, average='weighted')
+
+    # Create a pandas DataFrame with the evaluation metrics
+    crf_evaluation_metrics = pd.DataFrame({
+        'accuracy': [accuracy],
+        'precision': [precision],
+        'recall': [recall],
+        'f1_score': [f1]
+    })
+
+    return tagger, crf_evaluation_metrics
+
+
 
 """ Second part of this script contains the codes for unsupervised ML models which does not use sentiment labels"""
 
@@ -123,7 +175,7 @@ from sklearn.feature_extraction.text import CountVectorizer
 from sklearn.decomposition import LatentDirichletAllocation
 import numpy as np 
 
[…]

### 2023-03-30 src/sentiment_analysis_epp/models/task_run_models.py

@@ -54,7 +54,7 @@ def task_preprocess_data():
 import pandas as pd
 import pickle
 from pathlib import Path
-from sentiment_analysis_epp.models.models import fit_logit_model, fit_naive_bayes, fit_svm
+from sentiment_analysis_epp.models.models import fit_logit_model, fit_naive_bayes, fit_svm, fit_crf
 import pytask
 from sklearn.model_selection import train_test_split
 from sklearn.feature_extraction.text import TfidfVectorizer
@@ -64,6 +64,7 @@ from sklearn.feature_extraction.text import TfidfVectorizer
     BLD / "python" / "models" / "logit_model.pkl",
     BLD / "python" / "models" / "naive_bayes_model.pkl",
     BLD / "python" / "models" / "svm_model.pkl",
+    BLD / "python" / "models" / "crf_model.pkl",
     BLD / "python" / "evaluation_metrics.csv",
 ])
 def task_run_models(depends_on, produces):
@@ -82,7 +83,7 @@ def task_run_models(depends_on, produces):
     logit_model, logit_evaluation = fit_logit_model(X_train, y_train, X_test, y_test)
     nb_model, nb_evaluation = fit_naive_bayes(X_train, y_train, X_test, y_test)
     svm_model, svm_evaluation = fit_svm(X_train, y_train, X_test, y_test)
-
+    crf_model, crf_evaluation = fit_crf(X_train, y_train, X_test, y_test)
     # Save models
     with open(produces[0], "wb") as f:
         pickle.dump(logit_model, f)
@@ -90,23 +91,24 @@ def task_run_models(depends_on, produces):
         pickle.dump(nb_model, f)
     with open(produces[2], "wb") as f:
         pickle.dump(svm_model, f)
+    with open(produces[3], "wb") as f:
+        pickle.dump(crf_model, f)
+
 
     # Save evaluation metrics
-    evaluation_metrics = pd.concat([logit_evaluation, nb_evaluation, svm_evaluation], axis=0)
-    evaluation_metrics.index = ["logit", "naive_bayes", "svm"]
+    evaluation_metrics = pd.concat([logit_evaluation, nb_evaluation, svm_evaluation, crf_evaluation], axis=0)
+    evaluation_metrics.index = ["logit", "naive_bayes", "svm", "crf"]
     evaluation_metrics.to_csv(produces[3], index_label="Model")
 
     return None
 
 
+
[…]

### 2023-03-30 src/sentiment_analysis_epp/paper/paper.tex
updated the .tex file with new chapters, and modified the functions and tasks related to CRF

@@
-\documentclass[12pt]{article}
+\documentclass{article}
+\documentclass[12pt,a4paper]{article}
+\renewcommand{\baselinestretch}{1.5}
+\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
+\usepackage{datetime} 
+\newdateformat{monthyear}{%
+  \monthname[\THEMONTH], \THEYEAR}
 
-% Packages
-\usepackage[margin=1in]{geometry} % Set margins
-\usepackage{times} % Use Times New Roman font
-\usepackage{graphicx} % For including figures
-\usepackage{amsmath} % For math equations
-\usepackage{natbib} % For bibliography
+\usepackage{graphicx}
 
+\usepackage{natbib} % need for nice bibliography
+\usepackage{xcolor}
+\usepackage[colorlinks = true,
+            linkcolor = blue,
+            urlcolor  = blue,
+            citecolor = blue,
+            anchorcolor = blue]{hyperref}
+
+%__________________
+
+% Language setting
+% Replace `english' with e.g. `spanish' to change the document language
+%\usepackage[english]{babel}
+
+% Set page size and margins
+% Replace `letterpaper' with `a4paper' for UK/EU standard size
+%\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=3cm]{geometry}
+%\usepackage{setspace}
+%\setstretch{1.6}
+
+% Useful packages
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
 % Title
-\title{Sentiment Analysis in Python Using Kaggle Data}
+\title{Sentiment Analysis in Python Using Kaggle Dataset}
 \author{Ozodbek Ozodov}
@@
 \section{Literature Review}
+
 Several studies have been conducted to explore the potential of sentiment analysis in predicting stock market trends and financial performance.
 However, there are still many challenges in this field, including the lack of labeled data, the complexity of financial data, and the difficulty of achieving high accuracy in predicting stock prices.
-\\
+
 Pang, B. and Lee, L. (2008). Opinion mining and sentiment analysis. Foundations and Trends® in Information Retrieval, 2(1-2), pp.1-135.
@@
 It also discusses challenges in the field such as sarcasm and irony detection, and provides a list of publicly available sentiment analysis datasets.
-\\
+
 Socher, R., Perelygin, A., Wu, J.Y., Chuang, J., Manning, C.D., Ng, A.
@@
 The model achieved state-of-the-art performance on the Stanford Sentiment Treebank dataset, and the method of building a parse tree has since become a common approach in deep learning for natural language processing.
-\\
+
 Mohammad, S.M.
@@
 \section{Methodology}
+
 The overall research goal of this project is to build and evaluate machine learning models for sentiment analysis using a Kaggle dataset of financial news headlines.
@@
 
+\subsection{Logistic Regression}
+
+Logistic regression is a popular statistical model that is commonly used in machine learning for binary classification problems.
+It models the probability of a binary outcome, such as the sentiment of a financial news headline being positive, negative, or neutral, based on one or more predictor variables.
+The logistic regression model is based on the logistic function, which transforms the linear combination of the predictor variables into a probability value between 0 and 1.
+
+The logistic function is defined as:
+
+\sigma (z) = \frac{1}{1+e^{-z}}
+
+where:
+
+z = \beta_0+\beta_1x_1 + \beta_2x_2+...+\beta_p x_p
+
+The coefficients β are estimated using maximum likelihood estimation, which seeks to find the values of β that maximize the likelihood of the observed data given the model.
+
+In the case of financial news sentiment analysis, logistic regression can be used to classify headlines as positive, negative, or neutral based on the presence of certain keywords or phrases.
+To use logistic regression for this task, each headline is first represented numerically as a vector of features, where each feature represents the presence or absence of a particular keyword or phrase.
+These features are then used as the input to the logistic regression model, which outputs a probability for each class label.
+
+The logistic regression model works by fitting a logistic function to the input features.
+The logistic function transforms the linear combination of the input features and their corresponding coefficients into a probability value between 0 and 1.
+The coefficients are learned through a process called maximum likelihood estimation, which seeks to find the values of the coefficients that maximize the likelihood of the observed data given the model.
+
+One advantage of logistic regression is its simplicity and interpretability.
+The coefficients learned by the model can be used to identify which features are most important for predicting each class label.
+Furthermore, logistic regression can handle both categorical and continuous input features, making it a versatile modeling approach.
+
+However, logistic regression also has some limitations.
+For instance, it assumes that the relationship between the input features and the output variable is linear, which may not always be the case.
+Additionally, logistic regression may struggle with datasets that have a large number of input features or features that are highly correlated with each other.
+
+In summary, logistic regression is a widely-used approach for binary classification problems, such as financial news sentiment analysis.
+By representing each headline numerically and fitting a logistic function to the input features, logistic regression can accurately classify headlines as positive, negative, or neutral.
+While logistic regression has its limitations, it remains a useful and effective modeling technique for classification problems in finance and other fields.
+
+\subsection{Naive Bayes Classifier}
+
+Naive Bayes is a probabilistic machine learning algorithm that is commonly used in text classification tasks, such as sentiment analysis.
+The algorithm is based on Bayes' theorem, which describes the probability of an event occurring based on prior knowledge.
+
+In the context of financial news sentiment analysis, the Naive Bayes algorithm can be used to classify headlines as positive, negative, or neutral based on the presence of certain words or phrases.
+To use Naive Bayes for this task, each headline is first represented numerically as a vector of features, where each feature represents the presence or absence of a particular word or phrase.
+These features are then used as the input to the Naive Bayes model, which outputs a probability for each class label.
+
+The Naive Bayes algorithm works by making the assumption that the presence of a particular feature in a class is independent of the presence of other features in the same class.
+This is known as the "naive" assumption, and it simplifies the calculations required to estimate the probabilities of each class.
+
+Given a set of training examples, the Naive Bayes algorithm estimates the prior probability of each class, as well as the conditional probability of each feature given each class.
+These probabilities are then used to compute the posterior probability of each class given the input features using Bayes' theorem:
+
+P(c_i|x) = \frac{P(c_i) \prod^{n}_{j=1}P(x_k|c_i)}{\sum^{k}_{k=1}\prod^{n}_{j=1}P(x_j|c_k)}
+
+where $P(c_i|\mathbf{x})$ is the posterior probability of class $c_i$ given the input features $\mathbf{x}$, $P(c_i)$ is the prior probability of class $c_i$, $P(x_j|c_i)$ is the conditional probability of feature $x_j$ given class $c_i$, $n$ is the number of features, and $K$ is the number of classes.
+
+To classify a new headline, the Naive Bayes algorithm computes the posterior probability of each class given the input features and assigns the class with the highest probability as the predicted class label.
+
+One advantage of Naive Bayes is its simplicity and speed, as it requires relatively few training examples and can be trained efficiently on large datasets.
+However, Naive Bayes may not perform as well as more complex algorithms on datasets with highly correlated features or complex relationships between features and class labels.
+
+In summary, Naive Bayes is a probabilistic machine learning algorithm that is commonly used in text classification tasks, such as financial news sentiment analysis.
+By making the "naive" assumption that the presence of features is independent of each other, Naive Bayes can estimate the probabilities of each class given the input features using Bayes' theorem.
+While Naive Bayes is a simple and effective algorithm, it may not perform as well as more complex algorithms on certain datasets.
+
+\subsection{Support Vector Machines}
+
+Support Vector Machines (SVMs) are a powerful and widely used machine learning algorithm for classification and regression problems.
+In the context of sentiment analysis using financial news headlines, SVMs can be used to classify headlines as positive, negative, or neutral based on the presence of certain words or phrases.
+
+SVMs work by finding the hyperplane that maximally separates the different classes in the input feature space.
+In the case of sentiment analysis, each headline is first represented numerically as a vector of features, where each feature represents the presence or absence of a particular word or phrase.
+These features are then used as the input to the SVM model, which aims to find the hyperplane that best separates the different classes.
+
+Mathematically, the SVM model seeks to find the hyperplane that maximizes the margin between the classes, where the margin is defined as the distance between the hyperplane and the closest data points from each class.
+The hyperplane is defined as:
+
+w \cdot  x + b = 0
+
+where $\mathbf{w}$ is the weight vector, $\mathbf{x}$ is the input feature vector, and $b$ is the bias term.
+
+To train an SVM model, the algorithm seeks to find the optimal values of $\mathbf{w}$ and $b$ that maximize the margin between the classes while correctly classifying the training data.
+This is done by solving the following optimization problem:
+
+min_w,_b\frac{1}{2}||w||^2 $ subject to $ y_i(w) \dot x_i + b)\geq 1  $ for all $ i
+
+where $y_i$ is the class label of the $i$th data point and $|\mathbf{w}|^2$ is the L2 norm of the weight vector.
+
+In practice, the SVM model can also be extended to handle non-linearly separable data by using a kernel function to map the input features to a higher-dimensional space where the data is more easily separable.
+The most commonly used kernel functions are the linear kernel, polynomial kernel, and radial basis function (RBF) kernel.
+
+One advantage of SVMs is their ability to handle high-dimensional data and non-linear decision boundaries.
+SVMs are also known for their robustness to overfitting and their ability to handle noisy data.
+
+However, SVMs can be computationally intensive and require careful selection of hyperparameters, such as the choice of kernel function and the regularization parameter.
+
+In summary, Support Vector Machines are a powerful machine learning algorithm for classification problems, such as financial news sentiment analysis.
+By finding the hyperplane that maximizes the margin between the classes, SVMs can accurately classify headlines as positive, negative, or neutral based on the presence of certain words or phrases.
+While SVMs have certain advantages and limitations, they remain a popular and effective approach to classification problems in finance and other fields.
+
+\subsection{Conditional Random Field}
+
+Conditional Random Fields (CRFs) are a probabilistic graphical model that is widely used for sequence labeling tasks, such as named entity recognition and part-of-speech tagging.
+In the context of sentiment analysis using financial news headlines, CRFs can be used to label each word in the headline as positive, negative, or neutral based on the context of the entire headline.
+
+To use CRFs for this task, the input is typically represented as a sequence of words or tokens, where each token is associated with a set of features that capture the relevant information for sentiment analysis.
+These features might include the presence of certain keywords or phrases, as well as more complex features such as the part-of-speech or the dependency parse tree of the token.
+
+Mathematically, the CRF model defines a conditional probability distribution over the possible sequence labels given the input sequence of features.
+Specifically, the model computes the probability of a sequence of labels $\mathbf{y}$ given a sequence of features $\mathbf{x}$ as follows:
+
+P(y|x) = $\frac{1}{z(x)}$     exp\left\{\sum_{i=1}^{n} \sum_{j=1}^{k} w_i f_i (y_i, y_{i-1}, x,i)\right\}
+
+where $n$ is the length of the input sequence, $k$ is the number of unique transition features, $w_j$ is the weight parameter associated with the $j$th transition feature, $f_j(y_i, y_{i-1}, \mathbf{x}, i)$ is the value of the $j$th transition feature function for the labels $y_i$ and $y_{i-1}$ at position $i$ in the sequence, and $Z(\mathbf{x})$ is the normalization constant that ensures the probabilities sum to 1.
+
+The goal of training a CRF model is to estimate the optimal weight parameters that maximize the likelihood of the observed data.
+This is typically done using the maximum likelihood estimation method or its variants, such as the gradient descent algorithm.
+
+One advantage of CRFs is their ability to model dependencies between adjacent labels in the input sequence, which can capture the context and correlation between words in a sentence.
+Additionally, CRFs can handle both categorical and continuous input features, making them a versatile modeling approach.
+
+However, CRFs can be computationally expensive to train and may require careful feature engineering to achieve optimal performance.
+
+In summary, Conditional Random Fields are a probabilistic graphical model that is widely used for sequence labeling tasks, such as financial news sentiment analysis.
+By modeling the dependencies between adjacent labels in the input sequence, CRFs can accurately label each word in the headline as positive, negative, or neutral based on the context of the entire headline.
+While CRFs have certain advantages and limitations, they remain a popular and effective approach to sequence labeling problems in finance and other fields.
+
 % Results

### 2023-03-30 src/sentiment_analysis_epp/models/models.py

@@ -119,14 +119,16 @@ def fit_svm(X_train, y_train, X_test, y_test):
 
 import pycrfsuite
 import pandas as pd
+import numpy as np
 from sklearn.model_selection import train_test_split
 from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
 
 def fit_crf(X_train, y_train, X_test, y_test):
     def prepare_data_for_crf(X, y):
-        X_crf = X.apply(lambda x: [x.to_dict()], axis=1).tolist()
+        X_crf = pd.DataFrame(X.toarray()).apply(lambda x: x.to_dict(), axis=1).tolist()
         y_crf = y.apply(lambda x: [x]).tolist()
         return X_crf, y_crf
+
 
     # Prepare the data for CRF
     X_train_crf, y_train_crf = prepare_data_for_crf(X_train, y_train)
@@ -165,7 +167,6 @@ def fit_crf(X_train, y_train, X_test, y_test):
     })
 
     return tagger, crf_evaluation_metrics
-
 
 
 """ Second part of this script contains the codes for unsupervised ML models which does not use sentiment labels"""

### 2023-03-30 src/sentiment_analysis_epp/models/plots.py

@@ -1,0 +1,27 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+
+def plot_sentiment_hist(data_path, save_path=None):
+    # Load data
+    data = pd.read_csv(data_path)
+
+    # Count the number of sentiments for each class
+    sentiment_counts = data["Sentiment"].value_counts()
+
+    # Set up the figure
+    fig, ax = plt.subplots(figsize=(8, 6))
+
+    # Create the histogram
+    ax.bar(sentiment_counts.index, sentiment_counts.values, color=["#9b59b6", "#3498db", "#95a5a6"])
+
+    # Add labels and titles
+    ax.set_xlabel("Sentiment")
+    ax.set_ylabel("Number of Reviews")
+    ax.set_title("Distribution of Sentiments in Reviews")
+
+    # Save the figure if a save path is provided
+    if save_path:
+        fig.savefig(save_path, dpi=300, bbox_inches="tight")
+
+    # Show the figure
+    plt.show()

### 2023-03-30 src/sentiment_analysis_epp/models/task_run_models.py

@@ -4,9 +4,8 @@ import pytask
 import pandas as pd
 from sklearn.feature_extraction.text import CountVectorizer
 from pathlib import Path
-# from config import SRC
+
 SRC = Path(__file__).parent.resolve()
-#BLD = SRC.joinpath("..", "..", "bld").resolve()
 BLD = SRC.joinpath("..", "bld").resolve()
 
 # Add the src directory to the Python module search path

### 2023-03-31 src/sentiment_analysis_epp/config.py
updated tests, .tex file and tasks to optimize the process

@@ -7,3 +7,8 @@ BLD = SRC.joinpath("..", "..", "bld").resolve()
 PAPER_DIR = SRC.joinpath("..", "presentation_project_work").resolve()
 
 __all__ = ["BLD", "SRC", "PAPER_DIR"]
+
+from pytask import main
+
+if __name__ == "__main__":
+    main()

### 2023-03-31 src/sentiment_analysis_epp/models/models.py

@@ -125,9 +125,10 @@ from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_sc
 
 def fit_crf(X_train, y_train, X_test, y_test):
     def prepare_data_for_crf(X, y):
-        X_crf = pd.DataFrame(X.toarray()).apply(lambda x: x.to_dict(), axis=1).tolist()
-        y_crf = y.apply(lambda x: [x]).tolist()
+        X_crf = pd.DataFrame(X.toarray()).apply(lambda x: {str(k): v for k, v in x.to_dict().items()}, axis=1).tolist()
+        y_crf = [[str(label)] for label in y]
         return X_crf, y_crf
+
 
 
     # Prepare the data for CRF

### 2023-03-31 src/sentiment_analysis_epp/models/plots.py

@@ -1,12 +1,9 @@
 import pandas as pd
 import matplotlib.pyplot as plt
 
-def plot_sentiment_hist(data_path, save_path=None):
-    # Load data
-    data = pd.read_csv(data_path)
-
+def plot_sentiment_hist(df, save_path=None):
     # Count the number of sentiments for each class
-    sentiment_counts = data["Sentiment"].value_counts()
+    sentiment_counts = df["Sentiment"].value_counts()
 
     # Set up the figure
     fig, ax = plt.subplots(figsize=(8, 6))
@@ -22,6 +19,3 @@ def plot_sentiment_hist(data_path, save_path=None):
     # Save the figure if a save path is provided
     if save_path:
         fig.savefig(save_path, dpi=300, bbox_inches="tight")
-
-    # Show the figure
-    plt.show()

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -1,0 +1,27 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import seaborn as sns
+from pathlib import Path
+import pytask
+import os
+import sys
+sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..")))
+
+SRC = Path(__file__).parent.parent.resolve()
+BLD = SRC.joinpath("bld").resolve()
+
+from sentiment_analysis_epp.models.plots import plot_sentiment_hist
+
+@pytask.mark.depends_on(SRC / "sentiment_analysis_epp" / "data_management" / "data.csv")
+@pytask.mark.produces(BLD / "python" / "results" / "sentiment_histogram.png")
+def task_sentiment_histogram():
+    # Load the data
+    data_path = SRC / "sentiment_analysis_epp" / "data_management" / "data.csv"
+    df = pd.read_csv(data_path, encoding="ISO-8859-1")
+
+    # Create the plot and save it
+    plot_sentiment_hist(df)
+    output_path = BLD / "python" / "results" / "sentiment_histogram.png"
+    plt.savefig(output_path, dpi=300, bbox_inches="tight")
+
+    return None

### 2023-03-31 tests/test_import.py

@@ -1,7 +1,0 @@
-from __future__ import annotations
-
-import sentiment_analysis_epp
-
-
-def test_import():
-    assert hasattr(sentiment_analysis_epp, "__version__")

### 2023-03-31 tests/test_models.py

@@ -1,0 +1,213 @@
+from __future__ import annotations
+
+# import sentiment_analysis_epp
+
+import pandas as pd 
+import os
+import sys
+
+# Add the 'src' directory to the Python path
+sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..", "..", "src")))
+
+# Import the required functions from the 'models.py' module
+from sentiment_analysis_epp.models.models import preprocess_data
+import pandas as pd
+from sklearn.feature_extraction.text import CountVectorizer
+from sentiment_analysis_epp.models.models import preprocess_data
+
+def test_preprocess_data():
+    # Create a small DataFrame with sample data
+    data = pd.DataFrame({
+        'Text': ['I love this product', 'This is terrible'],
+        'Sentiment': [1, 0]
+    })
+
+    # Call the preprocess_data function
+    preprocessed_data = preprocess_data(data)
+
+    # Assert the presence of the 'bag_of_words' column
+    assert 'bag_of_words' in preprocessed_data.columns
+
+    # Assert that the length of the returned DataFrame is the same as the input
+    assert len(preprocessed_data) == len(data)
+
+    # Assert that the 'bag_of_words' column contains lists of strings
+    for item in preprocessed_data['bag_of_words']:
+        assert isinstance(item, list)
+        assert all(isinstance(i, str) for i in item)
+
+    # Assert that the bag of words representation is correct
+    vectorizer = CountVectorizer()
+    expected_bag_of_words = vectorizer.fit_transform(data['Text']).toarray()
+    expected_bag_of_words = [list(map(str, words)) for words in expected_bag_of_words]
+
+    assert all(a == b for a, b in zip(preprocessed_data['bag_of_words'], expected_bag_of_words))
+
+import numpy as np
+from sklearn.datasets import make_classification
+from sklearn.model_selection import train_test_split
+from sklearn.linear_model import LogisticRegression
+from sklearn.metrics import accuracy_score, precision_score, recall_score, f1_score
+from sentiment_analysis_epp.models.models import fit_logit_model
+
+
+def test_fit_logit_model():
+    # Create a small classification dataset
+    X, y = make_classification(n_samples=100, n_features=20, random_state=42)
+
+    # Split the dataset into training and testing sets
[…]

### 2023-03-31 src/sentiment_analysis_epp/models/models.py
updated outputs of the functions suitable for .tex, and broke some of tasks down into parts

@@ -24,6 +24,7 @@ def preprocess_data(data):
 
     return data
 
+from sklearn.metrics import confusion_matrix
 
 def fit_logit_model(X_train, y_train, X_test, y_test):
     # Fit the logistic regression model
@@ -38,16 +39,29 @@ def fit_logit_model(X_train, y_train, X_test, y_test):
     precision = precision_score(y_test, y_pred, average='weighted')
     recall = recall_score(y_test, y_pred, average='weighted')
     f1 = f1_score(y_test, y_pred, average='weighted')
+    from sklearn.metrics import confusion_matrix
+
+    def confusion_matrix_with_labels(y_true, y_pred, labels):
+        cm = confusion_matrix(y_true, y_pred, labels=["negative", "neutral", "positive"])
+        cm_df = pd.DataFrame(cm, index=labels, columns=labels)
+        row_sums = np.asarray(cm_df.sum(axis=1))
+        cm_df_percent = cm_df / row_sums[:, np.newaxis]
+        return cm_df_percent
+    conf_matrix_logit = confusion_matrix_with_labels(y_test, y_pred, labels=["negative", "neutral", "positive"])
 
     # Store the evaluation metrics in a dictionary
-    logit_model_evaluation = pd.DataFrame.from_dict({
+    logit_evaluation_metrics = pd.DataFrame.from_dict({
         "accuracy": [accuracy],
         "precision": [precision],
         "recall": [recall],
         "f1_score": [f1]
     })
 
-    return logit_model, logit_model_evaluation
+    # Store the confusion matrix in a separate DataFrame
+    conf_matrix_logit = pd.DataFrame(conf_matrix_logit)
+
+    return logit_model, logit_evaluation_metrics, conf_matrix_logit
+
 
 
 
@@ -66,6 +80,15 @@ def fit_naive_bayes(X_train, y_train, X_test, y_test):
     precision = precision_score(y_test, y_pred, average='weighted')
     recall = recall_score(y_test, y_pred, average='weighted')
     f1 = f1_score(y_test, y_pred, average='weighted')
+    from sklearn.metrics import confusion_matrix
+
+    def confusion_matrix_with_labels(y_true, y_pred, labels):
+        cm = confusion_matrix(y_true, y_pred, labels=["negative", "neutral", "positive"])
+        cm_df = pd.DataFrame(cm, index=labels, columns=labels)
+        row_sums = np.asarray(cm_df.sum(axis=1))
[…]

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -5,6 +5,7 @@ from pathlib import Path
 import pytask
 import os
 import sys
+"""
 sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..")))
 
 SRC = Path(__file__).parent.parent.resolve()
@@ -25,3 +26,4 @@ def task_sentiment_histogram():
     plt.savefig(output_path, dpi=300, bbox_inches="tight")
 
     return None
+"""

### 2023-03-31 src/sentiment_analysis_epp/models/task_run_models.py

@@ -4,6 +4,7 @@ import pytask
 import pandas as pd
 from sklearn.feature_extraction.text import CountVectorizer
 from pathlib import Path
+from sklearn.model_selection import train_test_split
 
 SRC = Path(__file__).parent.resolve()
 BLD = SRC.joinpath("..", "bld").resolve()
@@ -21,6 +22,8 @@ import pickle
 from sklearn.feature_extraction.text import CountVectorizer
 from pathlib import Path
 import pytask
+from sklearn.feature_extraction.text import TfidfVectorizer
+
 
 SRC = Path(__file__).resolve().parent.parent
 BLD = SRC / "bld"
@@ -50,23 +53,16 @@ def task_preprocess_data():
     return None
 
 
-import pandas as pd
 import pickle
-from pathlib import Path
-from sentiment_analysis_epp.models.models import fit_logit_model, fit_naive_bayes, fit_svm, fit_crf
-import pytask
-from sklearn.model_selection import train_test_split
-from sklearn.feature_extraction.text import TfidfVectorizer
+import pandas as pd
 
 @pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
 @pytask.mark.produces([
     BLD / "python" / "models" / "logit_model.pkl",
-    BLD / "python" / "models" / "naive_bayes_model.pkl",
-    BLD / "python" / "models" / "svm_model.pkl",
-    BLD / "python" / "models" / "crf_model.pkl",
-    BLD / "python" / "evaluation_metrics.csv",
+    BLD / "python" / "evaluation_metrics_logit.csv",
+    BLD / "python" / "conf_matrix_logit.tex"
 ])
-def task_run_models(depends_on, produces):
+def task_run_logit(depends_on, produces):
     # Load preprocessed data
     with open(depends_on, "rb") as f:
         data = pickle.load(f)
@@ -78,48 +74,82 @@ def task_run_models(depends_on, produces):
     # Train/test split
     X_train, X_test, y_train, y_test = train_test_split(X, data['Sentiment'], random_state=42)
 
-    # Fit models
-    logit_model, logit_evaluation = fit_logit_model(X_train, y_train, X_test, y_test)
-    nb_model, nb_evaluation = fit_naive_bayes(X_train, y_train, X_test, y_test)
-    svm_model, svm_evaluation = fit_svm(X_train, y_train, X_test, y_test)
[…]

### 2023-03-31 src/sentiment_analysis_epp/models/plots.py
updated plots and added plot_performance function and task which saves .png file in results folder

@@ -1,6 +1,10 @@
 import pandas as pd
 import matplotlib.pyplot as plt
 
+import sys
+print("Importing module:", __name__)
+
+
 def plot_sentiment_hist(df, save_path=None):
     # Count the number of sentiments for each class
     sentiment_counts = df["Sentiment"].value_counts()
@@ -19,3 +23,41 @@ def plot_sentiment_hist(df, save_path=None):
     # Save the figure if a save path is provided
     if save_path:
         fig.savefig(save_path, dpi=300, bbox_inches="tight")
+
+
+import os
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def plot_performance(input_file, output_file):
+    df = pd.read_csv(input_file)
+
+    models = df.iloc[:, 0]
+    metrics = df.iloc[:, 1:].astype(float)
+    accuracy = metrics['accuracy']
+    precision = metrics['precision']
+    recall = metrics['recall']
+    f1_score = metrics['f1_score']
+
+    barWidth = 0.2
+
+    r1 = np.arange(len(models))
+    r2 = [x + barWidth for x in r1]
+    r3 = [x + barWidth for x in r2]
+    r4 = [x + barWidth for x in r3]
+
+    plt.bar(r1, accuracy, color='royalblue', width=barWidth, edgecolor='white', label='Accuracy')
+    plt.bar(r2, precision, color='lightsteelblue', width=barWidth, edgecolor='white', label='Precision')
+    plt.bar(r3, recall, color='cornflowerblue', width=barWidth, edgecolor='white', label='Recall')
+    plt.bar(r4, f1_score, color='steelblue', width=barWidth, edgecolor='white', label='F1 Score')
+
+    plt.xticks([r + barWidth for r in range(len(models))], models)
+    plt.legend()
+    plt.savefig(output_file)
+    plt.show()
+    plt.legend(bbox_to_anchor=(1.05, 1), loc='upper left')
+    plt.savefig(output_file, format='png', dpi=300)
+    plt.show()

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -27,3 +27,28 @@ def task_sentiment_histogram():
 
     return None
 """
+import os
+import sys
+from pathlib import Path
+
+sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..", "..", "src")))
+import pytask
+from sentiment_analysis_epp.models.plots import plot_performance
+
+SRC = Path(__file__).resolve().parent.parent
+BLD = SRC / "bld"
+
+@pytask.mark.depends_on(
+    {
+        SRC / "bld" / "python" / "evaluation_metrics.csv",
+    })
+@pytask.mark.produces(BLD / "python" / "results" / "sentiment_histogram.png")
+def task_plot_performance(depends_on, produces):
+    # Define the input file containing the evaluation metrics
+    input_file = depends_on[0]
+
+    # Define the output file where the plot will be saved
+    output_file = produces
+
+    # Call the plot_performance() function to create the plot
+    plot_performance(input_file, output_file)

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py
optimized the plots, unified location of png files and fixed minor bugs

@@ -1,32 +1,24 @@
-import matplotlib.pyplot as plt
-import pandas as pd
-import seaborn as sns
-from pathlib import Path
 import pytask
-import os
-import sys
-"""
-sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..")))
-
-SRC = Path(__file__).parent.parent.resolve()
-BLD = SRC.joinpath("bld").resolve()
-
+from pathlib import Path
+import pandas as pd
 from sentiment_analysis_epp.models.plots import plot_sentiment_hist
 
-@pytask.mark.depends_on(SRC / "sentiment_analysis_epp" / "data_management" / "data.csv")
-@pytask.mark.produces(BLD / "python" / "results" / "sentiment_histogram.png")
-def task_sentiment_histogram():
-    # Load the data
-    data_path = SRC / "sentiment_analysis_epp" / "data_management" / "data.csv"
+SRC = Path(__file__).resolve().parent.parent
+BLD = SRC / "bld"
+
+@pytask.mark.depends_on(SRC / "data_management" / "data.csv")
+@pytask.mark.produces(BLD / "python" / "results" / "sentiment_hist.png")
+def task_plot_sentiment_hist(depends_on, produces):
+    data_path = depends_on
+    output_path = produces
+
+    # Read the data into a DataFrame
     df = pd.read_csv(data_path, encoding="ISO-8859-1")
 
-    # Create the plot and save it
-    plot_sentiment_hist(df)
-    output_path = BLD / "python" / "results" / "sentiment_histogram.png"
-    plt.savefig(output_path, dpi=300, bbox_inches="tight")
+    # Call the plot_sentiment_hist() function to create the plot
+    plot_sentiment_hist(df, save_path=output_path)
 
-    return None
-"""
+""" Model performance plot """
 import os
 import sys
 from pathlib import Path
@@ -42,7 +34,7 @@ BLD = SRC / "bld"
     {
         SRC / "bld" / "python" / "evaluation_metrics.csv",
     })
-@pytask.mark.produces(BLD / "python" / "results" / "sentiment_histogram.png")
+@pytask.mark.produces(BLD / "python" / "results" / "performance_bar.png")
 def task_plot_performance(depends_on, produces):
     # Define the input file containing the evaluation metrics
     input_file = depends_on[0]

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py
saving current state before checking out to new branch

@@ -31,9 +31,9 @@ SRC = Path(__file__).resolve().parent.parent
 BLD = SRC / "bld"
 
 @pytask.mark.depends_on(
-    {
-        SRC / "bld" / "python" / "evaluation_metrics.csv",
-    })
+    [
+        BLD / "python" / "evaluation_metrics.csv"
+    ])
 @pytask.mark.produces(BLD / "python" / "results" / "performance_bar.png")
 def task_plot_performance(depends_on, produces):
     # Define the input file containing the evaluation metrics

### 2023-03-31 src/sentiment_analysis_epp/models/task_run_models.py

@@ -92,6 +92,11 @@ def task_run_logit(depends_on, produces):
     return None
 @pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
 @pytask.mark.produces(BLD / "python" / "models" / "naive_bayes_model.pkl")
+@pytask.mark.produces([
+    BLD / "python" / "models" / "naive_bayes_model.pkl",
+    BLD / "python" / "evaluation_metrics_nb.csv",
+    BLD / "python" / "conf_matrix_nb.tex"
+])
 def task_run_naive_bayes(depends_on, produces):
     # Load preprocessed data
     with open(depends_on, "rb") as f:
@@ -153,3 +158,30 @@ def task_run_svm(depends_on, produces):
     conf_matrix_svm.style.to_latex(produces[2])
 
     return None
+
+import pytask
+from pathlib import Path
+import pandas as pd
+from sentiment_analysis_epp.models.plots import plot_sentiment_hist
+
+SRC = Path(__file__).resolve().parent
+BLD = SRC / "bld" / "python"
+
+@pytask.mark.depends_on([
+    BLD / "data" / "preprocessed_data.pkl",
+    BLD / "python" / "evaluation_metrics_logit.csv",
+    BLD / "python" / "evaluation_metrics_nb.csv",
+    BLD / "python" / "evaluation_metrics_svm.csv",
+])
+@pytask.mark.produces(BLD / "python" / "evaluation_metrics.csv")
+def task_evaluation_metrics(depends_on, produces):
+    # Read in the evaluation metrics for each model
+    logit_metrics = pd.read_csv(depends_on[1], index_col="Model")
+    nb_metrics = pd.read_csv(depends_on[2], index_col="Model")
+    svm_metrics = pd.read_csv(depends_on[3], index_col="Model")
+
+    # Concatenate the evaluation metrics DataFrames
+    combined_metrics = pd.concat([logit_metrics, nb_metrics, svm_metrics])
+
+    # Save the combined evaluation metrics as a CSV file
+    combined_metrics.to_csv(produces, index_label="Model")

### 2023-03-31 src/sentiment_analysis_epp/models/models.py
fixed the bug in bar graph of sentiment counts

@@ -162,7 +162,7 @@ def evaluation_metrics(logit_evaluation_metrics, nb_evaluation_metrics, svm_eval
     )
 
     # Set the index to model names
-    combined_evaluation_metrics.index = ["logit", "naive_bayes", "svm"]
+    combined_evaluation_metrics.index = ["Logistic regression", "Naive Bayes classifier", "Support Vector Machines"]
 
     # Save the combined evaluation metrics as a CSV file
     combined_evaluation_metrics.to_csv(output_csv_path, index_label="Model")

### 2023-03-31 src/sentiment_analysis_epp/models/plots.py

@@ -1,5 +1,7 @@
 import pandas as pd
 import matplotlib.pyplot as plt
+import sys
+
 
 def plot_sentiment_hist(df, save_path=None):
     # Count the number of sentiments for each class
@@ -9,7 +11,7 @@ def plot_sentiment_hist(df, save_path=None):
     fig, ax = plt.subplots(figsize=(8, 6))
 
     # Create the histogram
-    ax.bar(sentiment_counts.index, sentiment_counts.values, color=["#9b59b6", "#3498db", "#95a5a6"])
+    ax.bar(sentiment_counts.index, sentiment_counts.values, color=["#95a5a6", "#95a5a6", "#95a5a6"])
 
     # Add labels and titles
     ax.set_xlabel("Sentiment")
@@ -19,3 +21,41 @@ def plot_sentiment_hist(df, save_path=None):
     # Save the figure if a save path is provided
     if save_path:
         fig.savefig(save_path, dpi=300, bbox_inches="tight")
+
+
+import os
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def plot_performance(input_file, output_file):
+    df = pd.read_csv(input_file)
+
+    models = df.iloc[:, 0]
+    metrics = df.iloc[:, 1:].astype(float)
+    accuracy = metrics['accuracy']
+    precision = metrics['precision']
+    recall = metrics['recall']
+    f1_score = metrics['f1_score']
+
+    barWidth = 0.2
+
+    r1 = np.arange(len(models))
+    r2 = [x + barWidth for x in r1]
+    r3 = [x + barWidth for x in r2]
+    r4 = [x + barWidth for x in r3]
+
+    plt.bar(r1, accuracy, color='royalblue', width=barWidth, edgecolor='white', label='Accuracy')
+    plt.bar(r2, precision, color='lightsteelblue', width=barWidth, edgecolor='white', label='Precision')
+    plt.bar(r3, recall, color='cornflowerblue', width=barWidth, edgecolor='white', label='Recall')
+    plt.bar(r4, f1_score, color='steelblue', width=barWidth, edgecolor='white', label='F1 Score')
+
+    plt.xticks([r + barWidth for r in range(len(models))], models)
+    plt.legend()
+    plt.savefig(output_file)
+    plt.show()
+    plt.legend(bbox_to_anchor=(1.05, 1), loc='upper left')
+    plt.savefig(output_file, format='png', dpi=300)
+    plt.show()

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -1,29 +1,35 @@
-import matplotlib.pyplot as plt
 import pandas as pd
-import seaborn as sns
-from pathlib import Path
+import matplotlib.pyplot as plt
 import pytask
-import os
-import sys
-"""
-sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..")))
+from pathlib import Path
 
-SRC = Path(__file__).parent.parent.resolve()
-BLD = SRC.joinpath("bld").resolve()
+SRC = Path(__file__).resolve().parent.parent
+BLD = SRC / "bld"
 
-from sentiment_analysis_epp.models.plots import plot_sentiment_hist
-
-@pytask.mark.depends_on(SRC / "sentiment_analysis_epp" / "data_management" / "data.csv")
-@pytask.mark.produces(BLD / "python" / "results" / "sentiment_histogram.png")
-def task_sentiment_histogram():
+@pytask.mark.depends_on(SRC / "data_management" / "data.csv")
+@pytask.mark.produces(BLD / "plots" / "sentiment_hist.png")
+def task_sentiment_hist(depends_on, produces):
     # Load the data
-    data_path = SRC / "sentiment_analysis_epp" / "data_management" / "data.csv"
-    df = pd.read_csv(data_path, encoding="ISO-8859-1")
+    data = pd.read_csv(depends_on, encoding="ISO-8859-1")
 
-    # Create the plot and save it
-    plot_sentiment_hist(df)
-    output_path = BLD / "python" / "results" / "sentiment_histogram.png"
-    plt.savefig(output_path, dpi=300, bbox_inches="tight")
+    # Create the histogram plot
+    # Count the number of sentiments for each class
+    sentiment_counts = data["Sentiment"].value_counts()
+
+    # Set up the figure
+    fig, ax = plt.subplots(figsize=(8, 6))
+
+    # Create the histogram
+    ax.bar(sentiment_counts.index, sentiment_counts.values, color=["#9b59b6", "#3498db", "#95a5a6"])
+
+    # Add labels and titles
+    ax.set_xlabel("Sentiment")
+    ax.set_ylabel("Number of Reviews")
+    ax.set_title("Distribution of Sentiments in Reviews")
+
+    # Save the figure
+    fig.savefig(produces, dpi=300, bbox_inches="tight")
 
     return None
-"""
+
+

### 2023-03-31 src/sentiment_analysis_epp/models/task_run_models.py

@@ -91,7 +91,11 @@ def task_run_logit(depends_on, produces):
 
     return None
 @pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
-@pytask.mark.produces(BLD / "python" / "models" / "naive_bayes_model.pkl")
+@pytask.mark.produces([
+    BLD / "python" / "models" / "nb_model.pkl",
+    BLD / "python" / "evaluation_metrics_nb.csv",
+    BLD / "python" / "conf_matrix_nb.tex"]
+)
 def task_run_naive_bayes(depends_on, produces):
     # Load preprocessed data
     with open(depends_on, "rb") as f:
@@ -108,14 +112,14 @@ def task_run_naive_bayes(depends_on, produces):
     nb_model, nb_evaluation_metrics, conf_matrix_nb = fit_naive_bayes(X_train, y_train, X_test, y_test)
 
     # Save the model
-    with open(produces, "wb") as f:
+    with open(produces[0], "wb") as f:
         pickle.dump(nb_model, f)
 
     # Save the evaluation metrics
-    nb_evaluation_metrics.to_csv(BLD / "python" / "evaluation_metrics_nb.csv", index_label="Model")
+    nb_evaluation_metrics.to_csv(produces[1], index_label="Model")
 
     # Save the confusion matrix in latex format
-    with open(BLD / "python" / "confusion_matrix_nb.tex", "w") as f:
+    with open(produces[2], "w") as f:
         f.write(conf_matrix_nb.style.to_latex())
 
     return None
@@ -151,5 +155,35 @@ def task_run_svm(depends_on, produces):
 
     # Save the confusion matrix in LaTeX format
     conf_matrix_svm.style.to_latex(produces[2])
+
+    return None
+
+from sentiment_analysis_epp.models.models import  evaluation_metrics
+@pytask.mark.depends_on([
+    BLD / "python" / "evaluation_metrics_logit.csv",
+    BLD / "python" / "evaluation_metrics_nb.csv",
+    BLD / "python" / "evaluation_metrics_svm.csv"
+])
+@pytask.mark.produces([
+    BLD / "python" / "evaluation_metrics.csv",
+    BLD / "python" / "evaluation_metrics.tex"
+])
+def task_evaluation_metrics(depends_on, produces):
+    # Read the evaluation metrics CSV files for each model
+    logit_evaluation_metrics = pd.read_csv(depends_on[0], index_col="Model")
[…]

### 2023-03-31 src/sentiment_analysis_epp/models/plots.py
all plots and tasks are working properly in this setting, .tex file needs to be updated and compiled

@@ -3,7 +3,7 @@ import matplotlib.pyplot as plt
 import sys
 
 
-def plot_sentiment_hist(df, save_path=None):
+def plot_sentiment_bar(df, save_path=None):
     # Count the number of sentiments for each class
     sentiment_counts = df["Sentiment"].value_counts()
 
@@ -23,12 +23,9 @@ def plot_sentiment_hist(df, save_path=None):
         fig.savefig(save_path, dpi=300, bbox_inches="tight")
 
 
-import os
-import sys
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
-
 
 def plot_performance(input_file, output_file):
     df = pd.read_csv(input_file)
@@ -47,15 +44,18 @@ def plot_performance(input_file, output_file):
     r3 = [x + barWidth for x in r2]
     r4 = [x + barWidth for x in r3]
 
-    plt.bar(r1, accuracy, color='royalblue', width=barWidth, edgecolor='white', label='Accuracy')
-    plt.bar(r2, precision, color='lightsteelblue', width=barWidth, edgecolor='white', label='Precision')
-    plt.bar(r3, recall, color='cornflowerblue', width=barWidth, edgecolor='white', label='Recall')
-    plt.bar(r4, f1_score, color='steelblue', width=barWidth, edgecolor='white', label='F1 Score')
+    # Create a new figure for the second plot with transparent background
+    fig, ax = plt.subplots(figsize=(8, 6))
+    fig.patch.set_alpha(0.0)
 
-    plt.xticks([r + barWidth for r in range(len(models))], models)
-    plt.legend()
-    plt.savefig(output_file)
-    plt.show()
-    plt.legend(bbox_to_anchor=(1.05, 1), loc='upper left')
-    plt.savefig(output_file, format='png', dpi=300)
-    plt.show()
+    ax.bar(r1, accuracy, color='gray', hatch='////', width=barWidth, edgecolor='white', label='Accuracy')
+    ax.bar(r2, precision, color='gray', hatch='....', width=barWidth, edgecolor='white', label='Precision')
+    ax.bar(r3, recall, color='gray', hatch='xxxx', width=barWidth, edgecolor='white', label='Recall')
+    ax.bar(r4, f1_score, color='gray', hatch='++++', width=barWidth, edgecolor='white', label='F1 Score')
+    ax.set_ylim([0.7, 0.88])
[…]

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -6,30 +6,37 @@ from pathlib import Path
 SRC = Path(__file__).resolve().parent.parent
 BLD = SRC / "bld"
 
+from sentiment_analysis_epp.models.plots import plot_sentiment_bar
+
 @pytask.mark.depends_on(SRC / "data_management" / "data.csv")
 @pytask.mark.produces(BLD / "plots" / "sentiment_hist.png")
-def task_sentiment_hist(depends_on, produces):
+def task_sentiment_bar(depends_on, produces):
     # Load the data
     data = pd.read_csv(depends_on, encoding="ISO-8859-1")
 
     # Create the histogram plot
-    # Count the number of sentiments for each class
-    sentiment_counts = data["Sentiment"].value_counts()
-
-    # Set up the figure
-    fig, ax = plt.subplots(figsize=(8, 6))
-
-    # Create the histogram
-    ax.bar(sentiment_counts.index, sentiment_counts.values, color=["#9b59b6", "#3498db", "#95a5a6"])
-
-    # Add labels and titles
-    ax.set_xlabel("Sentiment")
-    ax.set_ylabel("Number of Reviews")
-    ax.set_title("Distribution of Sentiments in Reviews")
-
-    # Save the figure
-    fig.savefig(produces, dpi=300, bbox_inches="tight")
+    plot_sentiment_bar(data, save_path=produces)
 
     return None
 
+import pandas as pd
+import matplotlib.pyplot as plt
+import pytask
+from pathlib import Path
+import datetime
 
+SRC = Path(__file__).resolve().parent.parent
+BLD = SRC / "bld"
+
+from sentiment_analysis_epp.models.plots import plot_performance
+
+@pytask.mark.depends_on(SRC / "bld" / "python" / "evaluation_metrics.csv")
+@pytask.mark.produces(BLD / "plots" / f"performance_plot_{datetime.datetime.now().strftime('%Y%m%d_%H%M%S')}.png")
+def task_performance_plot(depends_on, produces):
+    # Call the plot_performance function
+    plot_performance(input_file=depends_on, output_file=produces)
+
+    # Clear the current figure to avoid overlapping with other plots
+    plt.clf()
+
+    return None

### 2023-03-31 tests/test_models.py

@@ -167,47 +167,3 @@ def test_fit_svm():
     assert np.isclose(svm_evaluation_metrics["precision"].values[0], precision)
     assert np.isclose(svm_evaluation_metrics["recall"].values[0], recall)
     assert np.isclose(svm_evaluation_metrics["f1_score"].values[0], f1)
-
-import pycrfsuite
-from sentiment_analysis_epp.models.models import fit_crf
-import scipy.sparse as sp
-
-
-def test_fit_crf():
-    # Create a small classification dataset
-    X, y = make_classification(n_samples=100, n_features=20, random_state=42)
-
-    # Convert the data into a sparse matrix
-    X_sparse = sp.csr_matrix(X)
-
-    # Split the dataset into training and testing sets
-    X_train, X_test, y_train, y_test = train_test_split(X_sparse, y, test_size=0.2, random_state=42)
-
-    # Call the fit_crf function
-    crf_model, crf_evaluation_metrics = fit_crf(X_train, y_train, X_test, y_test)
-
-    # Assert that the returned model is an instance of pycrfsuite.Tagger
-    assert isinstance(crf_model, pycrfsuite.Tagger)
-
-    # Assert that the returned evaluation is a DataFrame with the correct shape
-    assert isinstance(crf_evaluation_metrics, pd.DataFrame)
-    assert crf_evaluation_metrics.shape == (1, 4)
-
-    # Assert that the returned evaluation contains the correct columns
-    expected_columns = ["accuracy", "precision", "recall", "f1_score"]
-    assert all(col in crf_evaluation_metrics.columns for col in expected_columns)
-
-    # Evaluate the model on the test set
-    y_pred = [crf_model.tag(xseq)[0] for xseq in X_test]
-
-    # Compute evaluation metrics
-    accuracy = accuracy_score(y_test, y_pred)
-    precision = precision_score(y_test, y_pred, average='weighted')
-    recall = recall_score(y_test, y_pred, average='weighted')
-    f1 = f1_score(y_test, y_pred, average='weighted')
-
-    # Assert that the returned evaluation is correct
-    assert np.isclose(crf_evaluation_metrics["accuracy"].values[0], accuracy)
-    assert np.isclose(crf_evaluation_metrics["precision"].values[0], precision)
-    assert np.isclose(crf_evaluation_metrics["recall"].values[0], recall)
-    assert np.isclose(crf_evaluation_metrics["f1_score"].values[0], f1)

### 2023-03-31 src/sentiment_analysis_epp/models/plots.py
working state again, conflics are resolved

@@ -2,16 +2,12 @@ import pandas as pd
 import matplotlib.pyplot as plt
 import sys
 
-<<<<<<< HEAD
 import sys
 print("Importing module:", __name__)
 
 
-def plot_sentiment_hist(df, save_path=None):
-=======
-
 def plot_sentiment_bar(df, save_path=None):
->>>>>>> working-outputs
+
     # Count the number of sentiments for each class
     sentiment_counts = df["Sentiment"].value_counts()
 
@@ -31,19 +27,14 @@ def plot_sentiment_bar(df, save_path=None):
         fig.savefig(save_path, dpi=300, bbox_inches="tight")
 
 
-<<<<<<< HEAD
-import os
-import sys
-=======
->>>>>>> working-outputs
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
 
-<<<<<<< HEAD
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
 
-=======
->>>>>>> working-outputs
 def plot_performance(input_file, output_file):
     df = pd.read_csv(input_file)
 
@@ -61,20 +52,6 @@ def plot_performance(input_file, output_file):
     r3 = [x + barWidth for x in r2]
     r4 = [x + barWidth for x in r3]
 
-<<<<<<< HEAD
-    plt.bar(r1, accuracy, color='royalblue', width=barWidth, edgecolor='white', label='Accuracy')
-    plt.bar(r2, precision, color='lightsteelblue', width=barWidth, edgecolor='white', label='Precision')
-    plt.bar(r3, recall, color='cornflowerblue', width=barWidth, edgecolor='white', label='Recall')
-    plt.bar(r4, f1_score, color='steelblue', width=barWidth, edgecolor='white', label='F1 Score')
-
-    plt.xticks([r + barWidth for r in range(len(models))], models)
-    plt.legend()
-    plt.savefig(output_file)
-    plt.show()
-    plt.legend(bbox_to_anchor=(1.05, 1), loc='upper left')
-    plt.savefig(output_file, format='png', dpi=300)
-    plt.show()
-=======
     # Create a new figure for the second plot with transparent background
     fig, ax = plt.subplots(figsize=(8, 6))
     fig.patch.set_alpha(0.0)
@@ -90,4 +67,3 @@ def plot_performance(input_file, output_file):
     
     # Save the plot as a file
     fig.savefig(output_file, format='png', dpi=300, bbox_inches="tight", transparent=True)
->>>>>>> working-outputs

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -1,14 +1,13 @@
-<<<<<<< HEAD
 import pytask
 from pathlib import Path
 import pandas as pd
-from sentiment_analysis_epp.models.plots import plot_sentiment_hist
+from sentiment_analysis_epp.models.plots import plot_sentiment_bar
 
 SRC = Path(__file__).resolve().parent.parent
 BLD = SRC / "bld"
 
 @pytask.mark.depends_on(SRC / "data_management" / "data.csv")
-@pytask.mark.produces(BLD / "python" / "results" / "sentiment_hist.png")
+@pytask.mark.produces(BLD / "plots" / "sentiment_hist.png")
 def task_plot_sentiment_hist(depends_on, produces):
     data_path = depends_on
     output_path = produces
@@ -17,56 +16,9 @@ def task_plot_sentiment_hist(depends_on, produces):
     df = pd.read_csv(data_path, encoding="ISO-8859-1")
 
     # Call the plot_sentiment_hist() function to create the plot
-    plot_sentiment_hist(df, save_path=output_path)
+    plot_sentiment_bar(df, save_path=output_path)
 
 """ Model performance plot """
-import os
-import sys
-from pathlib import Path
-
-sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..", "..", "src")))
-import pytask
-from sentiment_analysis_epp.models.plots import plot_performance
-
-SRC = Path(__file__).resolve().parent.parent
-BLD = SRC / "bld"
-
-@pytask.mark.depends_on(
-    [
-        BLD / "python" / "evaluation_metrics.csv"
-    ])
-@pytask.mark.produces(BLD / "python" / "results" / "performance_bar.png")
-def task_plot_performance(depends_on, produces):
-    # Define the input file containing the evaluation metrics
-    input_file = depends_on[0]
-
-    # Define the output file where the plot will be saved
-    output_file = produces
-
-    # Call the plot_performance() function to create the plot
-    plot_performance(input_file, output_file)
-=======
-import pandas as pd
-import matplotlib.pyplot as plt
-import pytask
-from pathlib import Path
-
-SRC = Path(__file__).resolve().parent.parent
-BLD = SRC / "bld"
-
-from sentiment_analysis_epp.models.plots import plot_sentiment_bar
-
-@pytask.mark.depends_on(SRC / "data_management" / "data.csv")
[…]

### 2023-03-31 src/sentiment_analysis_epp/models/plots.py
conflicts are resolved

@@ -2,16 +2,8 @@ import pandas as pd
 import matplotlib.pyplot as plt
 import sys
 
-<<<<<<< HEAD
-import sys
-print("Importing module:", __name__)
-
-
-def plot_sentiment_hist(df, save_path=None):
-=======
 
 def plot_sentiment_bar(df, save_path=None):
->>>>>>> working-outputs
     # Count the number of sentiments for each class
     sentiment_counts = df["Sentiment"].value_counts()
 
@@ -31,19 +23,10 @@ def plot_sentiment_bar(df, save_path=None):
         fig.savefig(save_path, dpi=300, bbox_inches="tight")
 
 
-<<<<<<< HEAD
-import os
-import sys
-=======
->>>>>>> working-outputs
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
 
-<<<<<<< HEAD
-
-=======
->>>>>>> working-outputs
 def plot_performance(input_file, output_file):
     df = pd.read_csv(input_file)
 
@@ -61,20 +44,6 @@ def plot_performance(input_file, output_file):
     r3 = [x + barWidth for x in r2]
     r4 = [x + barWidth for x in r3]
 
-<<<<<<< HEAD
-    plt.bar(r1, accuracy, color='royalblue', width=barWidth, edgecolor='white', label='Accuracy')
-    plt.bar(r2, precision, color='lightsteelblue', width=barWidth, edgecolor='white', label='Precision')
-    plt.bar(r3, recall, color='cornflowerblue', width=barWidth, edgecolor='white', label='Recall')
-    plt.bar(r4, f1_score, color='steelblue', width=barWidth, edgecolor='white', label='F1 Score')
-
-    plt.xticks([r + barWidth for r in range(len(models))], models)
-    plt.legend()
-    plt.savefig(output_file)
-    plt.show()
-    plt.legend(bbox_to_anchor=(1.05, 1), loc='upper left')
-    plt.savefig(output_file, format='png', dpi=300)
-    plt.show()
-=======
     # Create a new figure for the second plot with transparent background
     fig, ax = plt.subplots(figsize=(8, 6))
     fig.patch.set_alpha(0.0)
@@ -90,4 +59,3 @@ def plot_performance(input_file, output_file):
     
     # Save the plot as a file
     fig.savefig(output_file, format='png', dpi=300, bbox_inches="tight", transparent=True)
->>>>>>> working-outputs

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py

@@ -1,51 +1,3 @@
-<<<<<<< HEAD
-import pytask
-from pathlib import Path
-import pandas as pd
-from sentiment_analysis_epp.models.plots import plot_sentiment_hist
-
-SRC = Path(__file__).resolve().parent.parent
-BLD = SRC / "bld"
-
-@pytask.mark.depends_on(SRC / "data_management" / "data.csv")
-@pytask.mark.produces(BLD / "python" / "results" / "sentiment_hist.png")
-def task_plot_sentiment_hist(depends_on, produces):
-    data_path = depends_on
-    output_path = produces
-
-    # Read the data into a DataFrame
-    df = pd.read_csv(data_path, encoding="ISO-8859-1")
-
-    # Call the plot_sentiment_hist() function to create the plot
-    plot_sentiment_hist(df, save_path=output_path)
-
-""" Model performance plot """
-import os
-import sys
-from pathlib import Path
-
-sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..", "..", "src")))
-import pytask
-from sentiment_analysis_epp.models.plots import plot_performance
-
-SRC = Path(__file__).resolve().parent.parent
-BLD = SRC / "bld"
-
-@pytask.mark.depends_on(
-    [
-        BLD / "python" / "evaluation_metrics.csv"
-    ])
-@pytask.mark.produces(BLD / "python" / "results" / "performance_bar.png")
-def task_plot_performance(depends_on, produces):
-    # Define the input file containing the evaluation metrics
-    input_file = depends_on[0]
-
-    # Define the output file where the plot will be saved
-    output_file = produces
-
-    # Call the plot_performance() function to create the plot
-    plot_performance(input_file, output_file)
-=======
 import pandas as pd
 import matplotlib.pyplot as plt
 import pytask
@@ -88,4 +40,3 @@ def task_performance_plot(depends_on, produces):
     plt.clf()
 
     return None
->>>>>>> working-outputs

### 2023-03-31 src/sentiment_analysis_epp/models/task_run_models.py

@@ -91,20 +91,11 @@ def task_run_logit(depends_on, produces):
 
     return None
 @pytask.mark.depends_on(SRC / "bld" / "python" / "data" / "preprocessed_data.pkl")
-<<<<<<< HEAD
-@pytask.mark.produces(BLD / "python" / "models" / "naive_bayes_model.pkl")
-@pytask.mark.produces([
-    BLD / "python" / "models" / "naive_bayes_model.pkl",
-    BLD / "python" / "evaluation_metrics_nb.csv",
-    BLD / "python" / "conf_matrix_nb.tex"
-])
-=======
 @pytask.mark.produces([
     BLD / "python" / "models" / "nb_model.pkl",
     BLD / "python" / "evaluation_metrics_nb.csv",
     BLD / "python" / "conf_matrix_nb.tex"]
 )
->>>>>>> working-outputs
 def task_run_naive_bayes(depends_on, produces):
     # Load preprocessed data
     with open(depends_on, "rb") as f:
@@ -167,34 +158,6 @@ def task_run_svm(depends_on, produces):
 
     return None
 
-<<<<<<< HEAD
-import pytask
-from pathlib import Path
-import pandas as pd
-from sentiment_analysis_epp.models.plots import plot_sentiment_hist
-
-SRC = Path(__file__).resolve().parent
-BLD = SRC / "bld" / "python"
-
-@pytask.mark.depends_on([
-    BLD / "data" / "preprocessed_data.pkl",
-    BLD / "python" / "evaluation_metrics_logit.csv",
-    BLD / "python" / "evaluation_metrics_nb.csv",
-    BLD / "python" / "evaluation_metrics_svm.csv",
-])
-@pytask.mark.produces(BLD / "python" / "evaluation_metrics.csv")
-def task_evaluation_metrics(depends_on, produces):
-    # Read in the evaluation metrics for each model
-    logit_metrics = pd.read_csv(depends_on[1], index_col="Model")
-    nb_metrics = pd.read_csv(depends_on[2], index_col="Model")
-    svm_metrics = pd.read_csv(depends_on[3], index_col="Model")
-
-    # Concatenate the evaluation metrics DataFrames
-    combined_metrics = pd.concat([logit_metrics, nb_metrics, svm_metrics])
-
-    # Save the combined evaluation metrics as a CSV file
-    combined_metrics.to_csv(produces, index_label="Model")
-=======
[…]

### 2023-03-31 src/sentiment_analysis_epp/paper/paper.tex
tasks are running except compilation

@@
 % Results
-\section{Results}
-This section should present the main findings of the research.
+\section{Results and Model Comparison}
+\subsection{Model Comparison}
+
+\input{../bld/python/evaluation_metrics.tex}
+
+The table shows the evaluation metrics of three models: Logistic Regression, Naive Bayes Classifier, and Support Vector Machines (SVM).
+All models achieved high accuracy scores, with SVM having the highest accuracy score of 0.7956.
+Precision and recall scores were also high for all models, with Logistic Regression and SVM having the highest precision and recall scores.
+The F1-score, which is the harmonic mean of precision and recall, was highest for Logistic Regression and SVM, indicating that they perform well in balancing precision and recall.
+Overall, the results suggest that all models perform well in predicting sentiment, with SVM performing slightly better than the other two models.
+
+\input{../src/sentiment_analysis_epp/bld/python/conf_matrix_logit.tex}
+
+The logit model has an overall accuracy of 72.1 percent, with the highest precision for the positive class (64.2 percent) and the highest recall for the neutral class (95.6 percent).
+The model performs relatively well in differentiating between the positive and negative classes, but struggles more with the neutral class.
+
+\input{../src/sentiment_analysis_epp/bld/python/conf_matrix_svm.tex}
+
+Support Vector Machines (SVM) model: The SVM model has a slightly higher overall accuracy of 73.4 percent, with the highest precision for the negative class (73.0 percent) and the highest recall for the neutral class (97.1 percent).
+The model also performs relatively well in differentiating between the positive and negative classes, but has lower precision and recall compared to the logit model for both classes.
+
+\input{../src/sentiment_analysis_epp/bld/python/conf_matrix_nb.tex}
+
+Naive Bayes model: The Naive Bayes model has the lowest overall accuracy of the three models at 60.4 percent, with the highest precision for the positive class (58.9 percent) and the highest recall for the neutral class (97.1 percent).
+This model performs relatively poorly in differentiating between the positive and negative classes, with low precision and recall for both classes.
 
@@
 \section{Discussion}
-This section should interpret and analyze the results, and discuss their implications.
+The results obtained from the three models indicate that all models have reasonable performance in classifying sentiments in the given dataset.
+However, there are some differences between the models in terms of their accuracy, precision, recall, and F1 score.
+
+The logistic regression and support vector machines models show similar performance, with slightly better results for the support vector machines model.
+On the other hand, the naive Bayes classifier has lower accuracy, precision, recall, and F1 score compared to the other models.
+
+One possible explanation for the differences in performance between the models is the complexity of the dataset.
+The dataset may have inherent complexities that make it difficult for the models to distinguish between the different sentiment classes.
+Another factor that could affect the performance is the choice of features and their representation.
+
+To improve the performance of the models, additional data preprocessing and feature engineering techniques can be employed.
+For example, a more comprehensive data cleaning process could be applied to reduce noise and improve the quality of the data.
+Additionally, more advanced feature selection and extraction techniques could be employed to identify the most important features for the classification task.
+
+While neural networks have shown significant success in various machine learning tasks, they were not used in this study due to their computational complexity and interpretability challenges.
+Neural networks require more computation power and time compared to traditional machine learning models, and the black-box nature of neural networks makes it difficult to interpret their decision-making process.
+
+In conclusion, the results obtained from the models indicate that sentiment analysis is a challenging task, and there is still room for improvement in the accuracy and performance of the models.
+However, with further refinement of data preprocessing techniques and feature engineering, it is possible to improve the performance of the models.
+Additionally, while neural networks have shown significant promise in various machine learning tasks, they were not used in this study due to their computational complexity and interpretability challenges.
 
@@
 \section{Conclusion}
-This section should summarize the main points of the paper and provide conclusions.
+
+In this project, I performed sentiment analysis on a dataset of online reviews using three different models: logistic regression, naive Bayes classifier, and support vector machines.
+I evaluated the performance of these models using four evaluation metrics: accuracy, precision, recall, and F1 score.
+
+The results showed that all three models achieved comparable performance in terms of accuracy, precision, recall, and F1 score.
+However, the logistic regression and support vector machines models slightly outperformed the naive Bayes classifier in terms of F1 score.
+
+One possible reason for the similar performance of the models could be the nature of the dataset, which contains short text reviews with a limited vocabulary.
+In such cases, simple models like logistic regression, naive Bayes classifier, and support vector machines can perform reasonably well.
+
+Another challenge I faced was the lack of interpretability of the models.
+While neural networks have been shown to outperform traditional machine learning models in various natural language processing tasks, they suffer from the challenge of interpretability.
+Therefore, I did not consider neural networks for sentiment analysis in this project.
+
+Overall, the findings suggest that simple machine learning models like logistic regression, naive Bayes classifier, and support vector machines can be effective for sentiment analysis tasks on short text reviews.
+Future work can focus on improving the performance of these models through feature engineering or exploring more sophisticated machine learning techniques.
 
@@
 \bibliographystyle{apa}
-\bibliography{references}
+\bibliography{refs}
+
+\begin{frame}[allowframebreaks]
+  \frametitle{References}
+  \renewcommand{\bibfont}{\normalfont\footnotesize}
+  \printbibliography
+\end{frame}
 
 \end{document}
+\end{document}

### 2023-03-31 src/sentiment_analysis_epp/paper/task_compile.py

@@ -1,0 +1,32 @@
+"""Tasks for compiling the paper of the sentiment analysis project."""
+from pathlib import Path
+import shutil
+import pytask
+from pytask_latex import compilation_steps as cs
+
+from sentiment_analysis_epp.config import BLD
+PAPER_DIR = Path(__file__).parent
+
+
+document = "paper"
+
+@pytask.mark.latex(
+    script=PAPER_DIR / f"{document}.tex",
+    document=BLD / "latex" / f"{document}.pdf",
+    compilation_steps=cs.latexmk(
+        options=("--pdf", "--interaction=nonstopmode", "--synctex=1", "--cd"),
+    ),
+)
+@pytask.mark.task(id=document)
+def task_compile_document():
+    """Compile the paper specified in the latex decorator."""
+
+kwargs = {
+    "depends_on": BLD / "latex" / f"{document}.pdf",
+    "produces": PAPER_DIR / f"{document}.pdf",
+}
+
+@pytask.mark.task(id=f"copy_{document}", kwargs=kwargs)
+def task_copy_to_root(depends_on, produces):
+    """Copy the compiled paper to the root directory."""
+    shutil.copy(depends_on, produces)

### 2023-03-31 src/sentiment_analysis_epp/paper/paper.tex
improved tests and tasks, all passing and running except compiling

@@
 \documentclass{article}
-\documentclass[12pt,a4paper]{article}
+\usepackage{hyperref}
+
 \renewcommand{\baselinestretch}{1.5}
@@
 \usepackage{datetime}
-\newdateformat{monthyear}{%
-  \monthname[\THEMONTH], \THEYEAR}
+
+\usepackage{mathtools}
+\usepackage{mathrsfs}
+\usepackage[utf8]{inputenc}
 
@@
 
-\usepackage{natbib} % need for nice bibliography
 \usepackage{xcolor}
@@
 This type of lexicon is useful for sentiment analysis, as it provides a way to quantify the emotional content of text beyond simply positive or negative sentiment.
+
+\section{Data}
+The data used in this study was obtained from Kaggle.com, a popular platform for sharing and discovering datasets.
+The initial dataset contained 3500 observations, with two columns: the financial news headline and its respective sentiment.
+However, due to an overabundance of neutral sentiments, which had the potential to lead to overfitting, 30\% of neutrals were randomly removed from the dataset.
+
+The remaining dataset had a very low percentage of negative sentiments (8\%), which would have negatively impacted the performance of the predictive algorithms used in this study.
+To address this issue, ChatGPT was utilized to generate negative sentiments and rebalance the dataset.
+As a result of these preprocessing steps, the final version of the dataset contained approximately 3100 observations.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics{src/sentiment_analysis_epp/bld/plots/sentiment_hist.png}
+  \caption{Histogram of sentiment values.}
+  \label{fig:sentiment_hist}
+\end{figure}
+
+Data preprocessing is carried out in three steps:
+
+Lemmatization: Lemmatization is the process of reducing a word to its base or root form, known as its lemma.
+For example, the word "am," "are," and "is" are all forms of the verb "to be" and can be reduced to the base form "be." By reducing words to their base form, we can simplify the text data and make it easier to analyze.
+
+Tokenization: Tokenization is the process of breaking text data into individual units or tokens, such as words or phrases.
+This is an important step in NLP because it allows us to analyze and manipulate the text on a granular level.
+Tokenization can be performed at various levels of granularity, such as word-level, sentence-level, or even character-level.
+
+Vectorizing: Vectorizing is the process of converting text data into a numerical representation that can be used by machine learning algorithms.
+One common technique for vectorizing text data is bag-of-words representation, which involves creating a matrix where each row represents a document, and each column represents a unique word in the corpus.
+The entries in the matrix are then the frequency of occurrence of the corresponding word in the corresponding document.
+Another common technique is using word embeddings, which maps each word to a vector of real numbers, so that similar words have similar vectors.
+
+Algorithms were used to analyze and predict the sentiment of the financial news headlines based on the numerical representation of the data.
+Overall, this study employed a rigorous approach to data cleaning, preprocessing, and analysis to ensure the accuracy and reliability of the findings.
+
 % Methodology
@@
 While SVMs have certain advantages and limitations, they remain a popular and effective approach to classification problems in finance and other fields.
-
-\subsection{Conditional Random Field}
-
-Conditional Random Fields (CRFs) are a probabilistic graphical model that is widely used for sequence labeling tasks, such as named entity recognition and part-of-speech tagging.
-In the context of sentiment analysis using financial news headlines, CRFs can be used to label each word in the headline as positive, negative, or neutral based on the context of the entire headline.
-
-To use CRFs for this task, the input is typically represented as a sequence of words or tokens, where each token is associated with a set of features that capture the relevant information for sentiment analysis.
-These features might include the presence of certain keywords or phrases, as well as more complex features such as the part-of-speech or the dependency parse tree of the token.
-
-Mathematically, the CRF model defines a conditional probability distribution over the possible sequence labels given the input sequence of features.
-Specifically, the model computes the probability of a sequence of labels $\mathbf{y}$ given a sequence of features $\mathbf{x}$ as follows:
-
-P(y|x) = $\frac{1}{z(x)}$     exp\left\{\sum_{i=1}^{n} \sum_{j=1}^{k} w_i f_i (y_i, y_{i-1}, x,i)\right\}
-
-where $n$ is the length of the input sequence, $k$ is the number of unique transition features, $w_j$ is the weight parameter associated with the $j$th transition feature, $f_j(y_i, y_{i-1}, \mathbf{x}, i)$ is the value of the $j$th transition feature function for the labels $y_i$ and $y_{i-1}$ at position $i$ in the sequence, and $Z(\mathbf{x})$ is the normalization constant that ensures the probabilities sum to 1.
-
-The goal of training a CRF model is to estimate the optimal weight parameters that maximize the likelihood of the observed data.
-This is typically done using the maximum likelihood estimation method or its variants, such as the gradient descent algorithm.
-
-One advantage of CRFs is their ability to model dependencies between adjacent labels in the input sequence, which can capture the context and correlation between words in a sentence.
-Additionally, CRFs can handle both categorical and continuous input features, making them a versatile modeling approach.
-
-However, CRFs can be computationally expensive to train and may require careful feature engineering to achieve optimal performance.
-
-In summary, Conditional Random Fields are a probabilistic graphical model that is widely used for sequence labeling tasks, such as financial news sentiment analysis.
-By modeling the dependencies between adjacent labels in the input sequence, CRFs can accurately label each word in the headline as positive, negative, or neutral based on the context of the entire headline.
-While CRFs have certain advantages and limitations, they remain a popular and effective approach to sequence labeling problems in finance and other fields.
-
 % Results
 \section{Results and Model Comparison}
-\subsection{Model Comparison}
 
-\input{../bld/python/evaluation_metrics.tex}
+\begin{figure}[htbp]
+  \centering
+  \includegraphics{src/sentiment_analysis_epp/bld/plots/performance_plot_*.png}
+  \caption{Caption text goes here.}
+  \label{fig:performance}
+\end{figure}
 
@@
 Overall, the results suggest that all models perform well in predicting sentiment, with SVM performing slightly better than the other two models.
+\\
 
-\input{../src/sentiment_analysis_epp/bld/python/conf_matrix_logit.tex}
+\input{src/sentiment_analysis_epp/bld/python/conf_matrix_logit.tex}
 
+\\
 The logit model has an overall accuracy of 72.1 percent, with the highest precision for the positive class (64.2 percent) and the highest recall for the neutral class (95.6 percent).
 The model performs relatively well in differentiating between the positive and negative classes, but struggles more with the neutral class.
+\\
 
-\input{../src/sentiment_analysis_epp/bld/python/conf_matrix_svm.tex}
+\input{src/sentiment_analysis_epp/bld/python/confusion_matrix_svm.tex}
 
+\\
 Support Vector Machines (SVM) model: The SVM model has a slightly higher overall accuracy of 73.4 percent, with the highest precision for the negative class (73.0 percent) and the highest recall for the neutral class (97.1 percent).
 The model also performs relatively well in differentiating between the positive and negative classes, but has lower precision and recall compared to the logit model for both classes.
+\\
 
-\input{../src/sentiment_analysis_epp/bld/python/conf_matrix_nb.tex}
+\input{src/sentiment_analysis_epp/bld/python/conf_matrix_nb.tex}
 
+\\
 Naive Bayes model: The Naive Bayes model has the lowest overall accuracy of the three models at 60.4 percent, with the highest precision for the positive class (58.9 percent) and the highest recall for the neutral class (97.1 percent).
@@
 
-% References
-\bibliographystyle{apa}
-\bibliography{refs}
+\newpage
+\pagebreak[]
 
-\begin{frame}[allowframebreaks]
-  \frametitle{References}
-  \renewcommand{\bibfont}{\normalfont\footnotesize}
-  \printbibliography
-\end{frame}
+References
+
+1.
+Rao, D.
+(2019).
+Multi-Class Text Classification with Scikit-Learn.
+Towards Data Science.
+Retrieved from \href{https://towardsdatascience.com/multi-class-text-classification-with-scikit-learn-12f1e60e0a9f.}
+
+2. Karambelkar, A. (2018). Stock News Sentiment Analysis with Python. Towards Data Science. Retrieved from \href{https://towardsdatascience.com/stock-news-sentiment-analysis-with-python-193d4b4378d4 }
+
+3.
+Schwartz, H.
+A., & Ungar, L.
+H.
+(2015).
+Data-Driven Content Analysis of Social Media: A Systematic Overview of Automated Methods.
+The Annals of the American Academy of Political and Social Science, 659, 78-94.
+
+4. Song, Z., & Xia, J. (2016). Spatial and Temporal Sentiment Analysis of Twitter data. In European Handbook of Crowdsourced Geographic Information (pp. 205-222). Ubiquity Press.
 
 \end{document}
-\end{document}

### 2023-03-31 src/sentiment_analysis_epp/models/models.py

@@ -172,3 +172,4 @@ def evaluation_metrics(logit_evaluation_metrics, nb_evaluation_metrics, svm_eval
 
     return latex_table
 
+

### 2023-03-31 src/sentiment_analysis_epp/paper/task_compile.py

@@ -1,4 +1,6 @@
 """Tasks for compiling the paper of the sentiment analysis project."""
+
+"""
 from pathlib import Path
 import shutil
 import pytask
@@ -19,7 +21,50 @@ document = "paper"
 )
 @pytask.mark.task(id=document)
 def task_compile_document():
+    
+
+kwargs = {
+    "depends_on": BLD / "latex" / f"{document}.pdf",
+    "produces": PAPER_DIR / f"{document}.pdf",
+}
+
+@pytask.mark.task(id=f"copy_{document}", kwargs=kwargs)
+def task_copy_to_root(depends_on, produces):
+    
+    shutil.copy(depends_on, produces)
+"""
+from pathlib import Path
+import shutil
+import pytask
+from pytask_latex import compilation_steps as cs
+
+from sentiment_analysis_epp.config import BLD
+
+PAPER_DIR = Path(__file__).parent
+
+document = "paper"
+
+@pytask.mark.latex(
+    script=PAPER_DIR / f"{document}.tex",
+    document=BLD / "latex" / f"{document}.pdf",
+    depends_on=[
+        BLD / "python" / "conf_matrix_nb.tex",
+        BLD / "python" / "data_description.tex",
+        BLD / "python" / "exploratory_data_analysis.tex",
+        BLD / "python" / "methodology.tex",
+        BLD / "python" / "results.tex",
+        BLD / "python" / "sentiment_analysis.py",
+        BLD / "python" / "sentiment_analysis_functions.py",
+        BLD / "python" / "topic_modelling.tex",
+    ],
+    compilation_steps=cs.latexmk(
+        options=("--pdf", "--interaction=nonstopmode", "--synctex=1", "--cd"),
+    ),
+)
+@pytask.mark.task(id=document)
+def task_compile_document():
     """Compile the paper specified in the latex decorator."""
+    pass
 
 kwargs = {
     "depends_on": BLD / "latex" / f"{document}.pdf",
@@ -30,3 +75,4 @@ kwargs = {
 def task_copy_to_root(depends_on, produces):
     """Copy the compiled paper to the root directory."""
     shutil.copy(depends_on, produces)
+

### 2023-03-31 tests/test_models.py

@@ -1,169 +1,190 @@
-from __future__ import annotations
-
-# import sentiment_analysis_epp
-
-import pandas as pd 
 import os
-import sys
-
-# Add the 'src' directory to the Python path
-sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), "..", "..", "src")))
-
-# Import the required functions from the 'models.py' module
-from sentiment_analysis_epp.models.models import preprocess_data
 import pandas as pd
+import pickle
 from sklearn.feature_extraction.text import CountVectorizer
 from sentiment_analysis_epp.models.models import preprocess_data
 
 def test_preprocess_data():
-    # Create a small DataFrame with sample data
-    data = pd.DataFrame({
-        'Text': ['I love this product', 'This is terrible'],
-        'Sentiment': [1, 0]
-    })
+    # Create a sample dataframe for testing
+    data = pd.DataFrame({'Text': ['This is a test', 'I love programming']})
 
     # Call the preprocess_data function
     preprocessed_data = preprocess_data(data)
 
-    # Assert the presence of the 'bag_of_words' column
+    # Check if the 'bag_of_words' column exists in the preprocessed data
     assert 'bag_of_words' in preprocessed_data.columns
 
-    # Assert that the length of the returned DataFrame is the same as the input
-    assert len(preprocessed_data) == len(data)
+    # Check if the 'bag_of_words' column has the correct data type (list of strings)
+    assert isinstance(preprocessed_data['bag_of_words'][0], list)
+    assert isinstance(preprocessed_data['bag_of_words'][0][0], str)
 
-    # Assert that the 'bag_of_words' column contains lists of strings
-    for item in preprocessed_data['bag_of_words']:
-        assert isinstance(item, list)
-        assert all(isinstance(i, str) for i in item)
+    # Check if the pickle file is created
+    assert os.path.exists('src/sentiment_analysis_epp/data_management/preprocessed_data.pkl')
 
-    # Assert that the bag of words representation is correct
-    vectorizer = CountVectorizer()
-    expected_bag_of_words = vectorizer.fit_transform(data['Text']).toarray()
-    expected_bag_of_words = [list(map(str, words)) for words in expected_bag_of_words]
+    # Load the pickle file and compare it with the preprocessed data
[…]

### 2023-03-31 tests/test_plots.py

@@ -1,0 +1,54 @@
+import os
+import pandas as pd
+import matplotlib.pyplot as plt
+from src.sentiment_analysis_epp.models.plots import plot_sentiment_bar
+
+def test_plot_sentiment_bar():
+    # Create a sample dataframe for testing
+    data = pd.DataFrame({'Text': ['This is a test', 'EPP was fun class'], 'Sentiment': ['neutral', 'positive']})
+
+    # Call the plot_sentiment_bar function
+    plot_sentiment_bar(data, save_path='test_plot_sentiment_bar.png')
+
+    # Check if the output file exists
+    assert os.path.exists('test_plot_sentiment_bar.png')
+
+    # Load the image and check if it has the expected dimensions
+    with open('test_plot_sentiment_bar.png', 'rb') as f:
+        img = plt.imread(f)
+
+    expected_height, expected_width, expected_channels = 1634, 2072, 4
+    assert img.shape == (expected_height, expected_width, expected_channels)
+
+    # Clean up the created image file
+    os.remove('test_plot_sentiment_bar.png')
+
+
+import os
+from src.sentiment_analysis_epp.models.plots import plot_performance
+
+import os
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from src.sentiment_analysis_epp.models.plots import plot_performance
+
+def test_plot_performance():
+    # Create a sample dataframe for testing
+    data = pd.DataFrame({'accuracy': [0.8, 0.7, 0.85], 'precision': [0.75, 0.8, 0.9], 'recall': [0.7, 0.75, 0.8], 'f1_score': [0.72, 0.78, 0.87]})
+    models = ["Logistic regression", "Naive Bayes classifier", "Support Vector Machines"]
+    data.index = models
+    data.index.name = "Model"
+    # Save the dataframe to a CSV file
+    data.to_csv('test_plot_performance.csv')
+
+    # Call the plot_performance function
+    plot_performance('test_plot_performance.csv', 'test_plot_performance.png')
+
+    # Check if the output file exists
+    assert os.path.exists('test_plot_performance.png')
+
+    # Clean up the created files
+    os.remove('test_plot_performance.csv')
+    os.remove('test_plot_performance.png')
+

### 2023-03-31 src/sentiment_analysis_epp/models/task_plot.py
modified compilation process, it is working with only one dependency now - the paper.tex file

@@ -31,7 +31,7 @@ BLD = SRC / "bld"
 from sentiment_analysis_epp.models.plots import plot_performance
 
 @pytask.mark.depends_on(SRC / "bld" / "python" / "evaluation_metrics.csv")
-@pytask.mark.produces(BLD / "plots" / f"performance_plot_{datetime.datetime.now().strftime('%Y%m%d_%H%M%S')}.png")
+@pytask.mark.produces(BLD / "plots" / "performance_plot.png")
 def task_performance_plot(depends_on, produces):
     # Call the plot_performance function
     plot_performance(input_file=depends_on, output_file=produces)

### 2023-03-31 src/sentiment_analysis_epp/paper/task_compile.py

@@ -1,78 +1,37 @@
-"""Tasks for compiling the paper of the sentiment analysis project."""
-
-"""
-from pathlib import Path
 import shutil
+from pathlib import Path
 import pytask
 from pytask_latex import compilation_steps as cs
 
-from sentiment_analysis_epp.config import BLD
-PAPER_DIR = Path(__file__).parent
+SRC = Path(__file__).parent.resolve()
+BLD = SRC.joinpath("..", "..", "bld").resolve()
 
+DEPS = [
+    BLD / "python" / "conf_matrix_logit.tex",
+    BLD / "python" / "conf_matrix_nb.tex",
+    BLD / "python" / "confusion_matrix_svm.tex",
+    BLD / "plots" / "sentiment_hist.png",
+    BLD / "plots" / "performance_plot_20230331_193625.png",
+]
 
-document = "paper"
+TEX_FILE = SRC / "paper.tex"
+PDF_FILE = BLD / "latex" / "paper_py.pdf"
+document = "paper_py"
 
 @pytask.mark.latex(
-    script=PAPER_DIR / f"{document}.tex",
-    document=BLD / "latex" / f"{document}.pdf",
+    script=TEX_FILE,
+    document=PDF_FILE,
     compilation_steps=cs.latexmk(
         options=("--pdf", "--interaction=nonstopmode", "--synctex=1", "--cd"),
     ),
 )
-@pytask.mark.task(id=document)
-def task_compile_document():
-    
+def task_compile_paper():
+    """Compile the paper using LaTeX."""
+kwargs = { "depends_on": SRC / "paper.tex",
+          "produces": BLD.parent.resolve() / "paper_py.pdf",
+}       
 
-kwargs = {
-    "depends_on": BLD / "latex" / f"{document}.pdf",
-    "produces": PAPER_DIR / f"{document}.pdf",
-}
-
-@pytask.mark.task(id=f"copy_{document}", kwargs=kwargs)
-def task_copy_to_root(depends_on, produces):
-    
+@pytask.mark.task(id=document, kwargs = kwargs)
+def task_copy_pdf_to_root(depends_on, produces):
+    """Copy the PDF file to the root directory."""
     shutil.copy(depends_on, produces)
-"""
-from pathlib import Path
-import shutil
-import pytask
-from pytask_latex import compilation_steps as cs
-
-from sentiment_analysis_epp.config import BLD
-
-PAPER_DIR = Path(__file__).parent
-
-document = "paper"
-
-@pytask.mark.latex(
[…]

### 2023-03-31 src/sentiment_analysis_epp/paper/paper.tex
initial checks are done

@@
 % Title
-\title{Sentiment Analysis in Python Using Kaggle Dataset}
+
+\title{Sentiment Analysis in Python Financial News Headlines}
 \author{Ozodbek Ozodov}
-\date{\today}
 
@@
 
-\begin{figure}[htbp]
-  \centering
-  \includegraphics{src/sentiment_analysis_epp/bld/plots/sentiment_hist.png}
-  \caption{Histogram of sentiment values.}
-  \label{fig:sentiment_hist}
-\end{figure}
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics{src/sentiment_analysis_epp/bld/plots/sentiment_hist.png}
+%  \caption{Histogram of sentiment values.}
+%  \label{fig:sentiment_hist}
+%\end{figure}
 
@@
 % Results
-\section{Results and Model Comparison}
+%\section{Results and Model Comparison}
 
-\begin{figure}[htbp]
-  \centering
-  \includegraphics{src/sentiment_analysis_epp/bld/plots/performance_plot_*.png}
-  \caption{Caption text goes here.}
-  \label{fig:performance}
-\end{figure}
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics[width=0.8\textwidth]{src/sentiment_analysis_epp/bld/plots/performance_plot.png}
+%  \caption{Caption text goes here.}
+%  \label{fig:performance}
+%\end{figure}
 
@@
 Overall, the results suggest that all models perform well in predicting sentiment, with SVM performing slightly better than the other two models.
-\\
 
-\input{src/sentiment_analysis_epp/bld/python/conf_matrix_logit.tex}
-
-\\
+%\input{src/sentiment_analysis_epp/bld/python/conf_matrix_logit.tex}
 The logit model has an overall accuracy of 72.1 percent, with the highest precision for the positive class (64.2 percent) and the highest recall for the neutral class (95.6 percent).
 The model performs relatively well in differentiating between the positive and negative classes, but struggles more with the neutral class.
-\\
-
-\input{src/sentiment_analysis_epp/bld/python/confusion_matrix_svm.tex}
-
-\\
+%\input{src/sentiment_analysis_epp/bld/python/confusion_matrix_svm.tex}
 Support Vector Machines (SVM) model: The SVM model has a slightly higher overall accuracy of 73.4 percent, with the highest precision for the negative class (73.0 percent) and the highest recall for the neutral class (97.1 percent).
 The model also performs relatively well in differentiating between the positive and negative classes, but has lower precision and recall compared to the logit model for both classes.
-\\
-
-\input{src/sentiment_analysis_epp/bld/python/conf_matrix_nb.tex}
-
-\\
+%\input{src/sentiment_analysis_epp/bld/python/conf_matrix_nb.tex}
 Naive Bayes model: The Naive Bayes model has the lowest overall accuracy of the three models at 60.4 percent, with the highest precision for the positive class (58.9 percent) and the highest recall for the neutral class (97.1 percent).

### 2023-03-31 src/sentiment_analysis_epp/paper/task_compile.py

@@ -1,3 +1,4 @@
+"""
 import shutil
 from pathlib import Path
 import pytask
@@ -26,12 +27,13 @@ document = "paper_py"
     ),
 )
 def task_compile_paper():
-    """Compile the paper using LaTeX."""
+   
 kwargs = { "depends_on": SRC / "paper.tex",
           "produces": BLD.parent.resolve() / "paper_py.pdf",
 }       
 
 @pytask.mark.task(id=document, kwargs = kwargs)
 def task_copy_pdf_to_root(depends_on, produces):
-    """Copy the PDF file to the root directory."""
+   
     shutil.copy(depends_on, produces)
+"""
